---
title: "Case study 3: Covid case study"
author: ""
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rstan)
library(ggplot2)
```

We investigate on K=10 different datasets and for 60, 100 and 200 number of data points.

```{r}
ndp = c(60,100,200)
K = 10
startSeed = 1
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)
```

Let's set the parameters for generating data:

```{r}
mu_U1_SARS_Ang = 22
sigma_U1_SARS_Ang = 10

mu_U2_SARS_Ang = 22
sigma_U2_SARS_Ang = 10

beta0_U_SARS_AngToSARS_COV2 = -2
beta_U1_SARS_AngToSARS_COV2 = 0.05 #positive
beta_U2_SARS_AngToSARS_COV2 = 0.06 #positive

beta0_SARS_COV2ToACE2 = 20
beta_SARS_COV2ToACE2 = -0.1 #negative

beta0_ACE2_and_U_SARS_Ang_ToAng = 25
beta_ACE2ToAng = -0.8 #negative
beta_U1_SARS_AngToAng = 0.5 #positive
beta_U2_SARS_AngToAng = 0.6 #positive

beta0_AngToAGTR1 = -1.5
beta_AngToAGTR1 = 0.08

mu_U1_ADAM17_Sil6r = 25
sigma_U1_ADAM17_Sil6r= 10

mu_U2_ADAM17_Sil6r = 25
sigma_U2_ADAM17_Sil6r= 10

beta0_AGTR1_UToADAM17 = -3.8
beta_AGTR1ToADAM17 = 0.04
beta_U1_ADAM17_Sil6rToADAM17 = 0.04
beta_U2_ADAM17_Sil6rToADAM17 = 0.03

mu_Toci = 45
sigma_Toci = 10

beta0_ADAM17_U_TociToSil6r = -3
beta_ADAM17ToSil6r = 0.03
beta_U1ToSil6r = 0.05
beta_U2ToSil6r = 0.06
beta_TociToSil6r = -0.04 #negative

mu_U_EGF_EGFR = 50
sigma_U_EGF_EGFR = 10

beta0_ADAM17_UToEGF = -3
beta_ADAM17ToEGF = 0.03
beta_UToEGF = 0.05

mu_U_EGFR_TNF = 45
sigma_U_EGFR_TNF = 10

beta0_ADAM17_UToTNF = -4.1
beta_ADAM17ToTNF = 0.05
beta_UToTNF = 0.06

mu_U_EGFR_IL6STAT3 = 40
sigma_U_EGFR_IL6STAT3 = 10

mu_Gefi = 40
sigma_Gefi = 10

beta0_EGF_3U = -6
beta_EGFToEGFR = 0.03
beta_U1ToEGFR = 0.05
beta_U2ToEGFR = 0.02
beta_U3ToEGFR = 0.04
beta_GefiToEGFR = -0.04 #negative

mu_U1_PRR_NFKB = 20
sigma_U1_PRR_NFKB = 10

mu_U2_PRR_NFKB = 20
sigma_U2_PRR_NFKB = 10

beta0_SARS_UPRR = -3.4
beta_SARS_COV2ToPRR = 0.05
beta_U1ToPRR = 0.02
beta_U2ToPRR = 0.03

beta0_PRR_U_EGFR_TNFToNFKB = -5
beta_PRRToNFKB = 0.01
beta_U1ToNFKB = 0.02
beta_U2ToNFKB = 0.03
beta_EGFRToNFKB = 0.02
beta_TNFToNFKB = 0.03

beta0_NFKB_IL6STSTToIL6STAT3 = -4.6
beta_UToIL6STAT3 = 0.05
beta_Sil6rToIL6STAT3 = 0.04

beta0_NFKB_IL6STATToIL6AMP = -3.7
beta_NFKBToIL6AMP = 0.02
beta_IL6STAT3ToIL6AMP = 0.03

beta0_IL6AMPTocytok = -2
beta_IL6AMPTocytok = 0.06
```


# Create observational data for Covid model

```{r}
obs_data_list <- list()
data_count = 1
for (seed in startSeed:(startSeed+K-1)) {
  set.seed(seed)
  U1_SARS_Ang <- rnorm(500, mu_U1_SARS_Ang, sigma_U1_SARS_Ang)
  U2_SARS_Ang <- rnorm(500, mu_U2_SARS_Ang, sigma_U2_SARS_Ang)
  SARS_COV2 = 100 / (1 + exp(-beta0_U_SARS_AngToSARS_COV2 -U1_SARS_Ang * beta_U1_SARS_AngToSARS_COV2 -U2_SARS_Ang * beta_U2_SARS_AngToSARS_COV2))
  Toci <- rnorm(500, mu_Toci, sigma_Toci)
  ACE2 = beta0_SARS_COV2ToACE2 + SARS_COV2 * beta_SARS_COV2ToACE2
  Ang = beta0_ACE2_and_U_SARS_Ang_ToAng + ACE2 * beta_ACE2ToAng + U1_SARS_Ang *beta_U1_SARS_AngToAng + U2_SARS_Ang *beta_U2_SARS_AngToAng
  AGTR1 = 100 / (1 + exp(-beta0_AngToAGTR1 - Ang * beta_AngToAGTR1))
  U1_ADAM17_Sil6r <- rnorm(500, mu_U1_ADAM17_Sil6r, sigma_U1_ADAM17_Sil6r)
  U2_ADAM17_Sil6r <- rnorm(500, mu_U2_ADAM17_Sil6r, sigma_U2_ADAM17_Sil6r)
  ADAM17 = 100 / (1 + exp(-beta0_AGTR1_UToADAM17 - AGTR1 * beta_AGTR1ToADAM17 - U1_ADAM17_Sil6r * beta_U1_ADAM17_Sil6rToADAM17 - U2_ADAM17_Sil6r * beta_U2_ADAM17_Sil6rToADAM17))
  Sil6r = 100 / (1 + exp(-beta0_ADAM17_U_TociToSil6r - ADAM17 * beta_ADAM17ToSil6r - U1_ADAM17_Sil6r * beta_U1ToSil6r - U2_ADAM17_Sil6r * beta_U2ToSil6r - Toci * beta_TociToSil6r))
  U_EGF_EGFR = rnorm(500, mu_U_EGF_EGFR, sigma_U_EGF_EGFR)
  EGF = 100 / (1 + exp(-beta0_ADAM17_UToEGF - ADAM17 * beta_ADAM17ToEGF - U_EGF_EGFR * beta_UToEGF))
  U_EGFR_TNF = rnorm(500, mu_U_EGFR_TNF, sigma_U_EGFR_TNF)
  TNF = 100 / (1 + exp(-beta0_ADAM17_UToTNF - ADAM17 * beta_ADAM17ToTNF - U_EGFR_TNF * beta_UToTNF))
  U_EGFR_IL6STAT3 <- rnorm(500, mu_U_EGFR_IL6STAT3, sigma_U_EGFR_IL6STAT3)
  Gefi <- rnorm(500, mu_Gefi, sigma_Gefi)
  EGFR = 100 / (1 + exp(-beta0_EGF_3U - EGF * beta_EGFToEGFR - U_EGFR_IL6STAT3 * beta_U1ToEGFR - U_EGFR_TNF * beta_U2ToEGFR  - U_EGF_EGFR * beta_U3ToEGFR - Gefi * beta_GefiToEGFR))
  U1_PRR_NFKB <- rnorm(500, mu_U1_PRR_NFKB, sigma_U1_PRR_NFKB)
  U2_PRR_NFKB <- rnorm(500, mu_U2_PRR_NFKB, sigma_U2_PRR_NFKB)
  PRR = 100 / (1 + exp(-beta0_SARS_UPRR - SARS_COV2 * beta_SARS_COV2ToPRR - U1_PRR_NFKB * beta_U1ToPRR - U2_PRR_NFKB * beta_U2ToPRR))
  NFKB = 100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR * beta_PRRToNFKB - U1_PRR_NFKB * beta_U1ToNFKB  - U2_PRR_NFKB * beta_U2ToNFKB- EGFR * beta_EGFRToNFKB  - TNF * beta_TNFToNFKB))
  IL6STAT3 = 100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3 * beta_UToIL6STAT3 - Sil6r * beta_Sil6rToIL6STAT3))
  IL6AMP = 100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB * beta_NFKBToIL6AMP - IL6STAT3 * beta_IL6STAT3ToIL6AMP))
  #cytok = 100 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP * beta_IL6AMPTocytok))
  p_cytok = 1 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP * beta_IL6AMPTocytok))
  cytok = rbinom(n = 500, size = 1, prob = p_cytok)
  observational_data <- data.frame("U1_SARS_Ang" = U1_SARS_Ang
                                   ,"U2_SARS_Ang" = U2_SARS_Ang
                  ,"SARS_COV2" = SARS_COV2
                  ,"ACE2" = ACE2
                  ,"Ang" = Ang
                  ,"AGTR1" = AGTR1
                  ,"U1_ADAM17_Sil6r" = U1_ADAM17_Sil6r
                  ,"U2_ADAM17_Sil6r" = U2_ADAM17_Sil6r
                  ,"ADAM17" = ADAM17
                  ,"Toci" = Toci
                  ,"Sil6r" = Sil6r
                  ,"U_EGF_EGFR" = U_EGF_EGFR
                  ,"EGF" = EGF
                  ,"U_EGFR_TNF" = U_EGFR_TNF
                  ,"TNF" = TNF
                  ,"U_EGFR_IL6STAT3" = U_EGFR_IL6STAT3
                  ,"Gefi" = Gefi
                  ,"EGFR" = EGFR
                  ,"U1_PRR_NFKB" = U1_PRR_NFKB
                  ,"U2_PRR_NFKB" = U2_PRR_NFKB
                  ,"PRR" = PRR
                  ,"NFKB" = NFKB
                  ,"IL6STAT3" = IL6STAT3
                  ,"IL6AMP" = IL6AMP
                  ,"cytok" = cytok)
  obs_data_list[[data_count]] <- observational_data
  data_count = data_count + 1
}
```


# Create interventional data for Covid model when Sil6ra is 20

```{r}
intv_data_list_sil6r <- list()
data_count = 1
for (seed in startSeed:(startSeed+K-1)) {
  set.seed(seed)
  U1_SARS_Ang <- obs_data_list[[data_count]]$U1_SARS_Ang
  U2_SARS_Ang <- obs_data_list[[data_count]]$U2_SARS_Ang
  SARS_COV2 = obs_data_list[[data_count]]$SARS_COV2
  ACE2 = obs_data_list[[data_count]]$ACE2
  Ang = obs_data_list[[data_count]]$Ang
  AGTR1 = obs_data_list[[data_count]]$AGTR1
  U1_ADAM17_Sil6r <- obs_data_list[[data_count]]$U1_ADAM17_Sil6r
  U2_ADAM17_Sil6r <- obs_data_list[[data_count]]$U2_ADAM17_Sil6r
  ADAM17 = obs_data_list[[data_count]]$ADAM17
  Toci =obs_data_list[[data_count]]$Toci
  Sil6r = 20
  U_EGF_EGFR = obs_data_list[[data_count]]$U_EGF_EGFR
  EGF = obs_data_list[[data_count]]$EGF
  U_EGFR_TNF = obs_data_list[[data_count]]$U_EGFR_TNF
  TNF = obs_data_list[[data_count]]$TNF
  U_EGFR_IL6STAT3 <- obs_data_list[[data_count]]$U_EGFR_IL6STAT3
  Gefi = obs_data_list[[data_count]]$Gefi
  EGFR = obs_data_list[[data_count]]$EGFR
  U1_PRR_NFKB <- obs_data_list[[data_count]]$U1_PRR_NFKB
  U2_PRR_NFKB <- obs_data_list[[data_count]]$U2_PRR_NFKB
  PRR = obs_data_list[[data_count]]$PRR
  NFKB = obs_data_list[[data_count]]$NFKB
  IL6STAT3 = 100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3 * beta_UToIL6STAT3 - Sil6r * beta_Sil6rToIL6STAT3))
  IL6AMP = 100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB * beta_NFKBToIL6AMP - IL6STAT3 * beta_IL6STAT3ToIL6AMP))
  #cytok = 100 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP * beta_IL6AMPTocytok))
  p_cytok = 1 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP * beta_IL6AMPTocytok))
  cytok = rbinom(n = 500, size = 1, prob = p_cytok)
  
  interventional_data_sil6r <- data.frame("U1_SARS_Ang" = U1_SARS_Ang
                                          ,"U2_SARS_Ang" = U2_SARS_Ang
                                          ,"SARS_COV2" = SARS_COV2
                                          ,"ACE2" = ACE2
                                          ,"Ang" = Ang
                                          ,"AGTR1" = AGTR1
                                          ,"U1_ADAM17_Sil6r" = U1_ADAM17_Sil6r
                                          ,"U2_ADAM17_Sil6r" = U2_ADAM17_Sil6r
                                          ,"ADAM17" = ADAM17
                                          ,"Toci" = Toci
                                          ,"Sil6r" = 20
                                          ,"U_EGF_EGFR" = U_EGF_EGFR
                                          ,"EGF" = EGF
                                          ,"U_EGFR_TNF" = U_EGFR_TNF
                                          ,"TNF" = TNF
                                          ,"U_EGFR_IL6STAT3" = U_EGFR_IL6STAT3
                                          ,"Gefi" = Gefi
                                          ,"EGFR" = EGFR
                                          ,"U1_PRR_NFKB" = U1_PRR_NFKB
                                          ,"U2_PRR_NFKB" = U2_PRR_NFKB
                                          ,"PRR" = PRR
                                          ,"NFKB" = NFKB
                                          ,"IL6STAT3" = IL6STAT3
                                          ,"IL6AMP" = IL6AMP
                                          ,"cytok" = cytok)
  intv_data_list_sil6r[[data_count]] <- interventional_data_sil6r
  data_count = data_count + 1
}
#54 parameters in total
```

# Create interventional data for Covid model when we intervene on EGFR = 20 

```{r}
intv_data_list_egfr <- list()
data_count = 1
for (seed in startSeed:(startSeed+K-1)) {
  set.seed(seed)
  U1_SARS_Ang <- obs_data_list[[data_count]]$U1_SARS_Ang
  U2_SARS_Ang <- obs_data_list[[data_count]]$U2_SARS_Ang
  SARS_COV2 = obs_data_list[[data_count]]$SARS_COV2
  ACE2 = obs_data_list[[data_count]]$ACE2
  Ang = obs_data_list[[data_count]]$Ang
  AGTR1 = obs_data_list[[data_count]]$AGTR1
  U1_ADAM17_Sil6r <- obs_data_list[[data_count]]$U1_ADAM17_Sil6r
  U2_ADAM17_Sil6r <- obs_data_list[[data_count]]$U2_ADAM17_Sil6r   
  ADAM17 = obs_data_list[[data_count]]$ADAM17
  Toci =obs_data_list[[data_count]]$Toci
  Sil6r = obs_data_list[[data_count]]$Sil6r
  U_EGF_EGFR = obs_data_list[[data_count]]$U_EGF_EGFR
  EGF = obs_data_list[[data_count]]$EGF
  U_EGFR_TNF = obs_data_list[[data_count]]$U_EGFR_TNF
  TNF = obs_data_list[[data_count]]$TNF
  U_EGFR_IL6STAT3 <- obs_data_list[[data_count]]$U_EGFR_IL6STAT3
  Gefi = obs_data_list[[data_count]]$Gefi
  U1_PRR_NFKB <- obs_data_list[[data_count]]$U1_PRR_NFKB
  U2_PRR_NFKB <- obs_data_list[[data_count]]$U2_PRR_NFKB
  PRR = obs_data_list[[data_count]]$PRR
  EGFR = 20
  NFKB = 100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR * beta_PRRToNFKB - U1_PRR_NFKB * beta_U1ToNFKB  - U2_PRR_NFKB * beta_U2ToNFKB - EGFR * beta_EGFRToNFKB  - TNF * beta_TNFToNFKB))
  IL6STAT3 = obs_data_list[[data_count]]$IL6STAT3
  IL6AMP = 100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB * beta_NFKBToIL6AMP - IL6STAT3 * beta_IL6STAT3ToIL6AMP))
  #cytok = 100 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP * beta_IL6AMPTocytok))
  p_cytok = 1 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP * beta_IL6AMPTocytok))
  cytok = rbinom(n = 500, size = 1, prob = p_cytok)
  
  interventional_data_egfr <- data.frame("U1_SARS_Ang" = U1_SARS_Ang
                                         ,"U2_SARS_Ang" = U2_SARS_Ang
                                         ,"SARS_COV2" = SARS_COV2
                                         ,"ACE2" = ACE2
                                         ,"Ang" = Ang
                                         ,"AGTR1" = AGTR1
                                         ,"U1_ADAM17_Sil6r" = U1_ADAM17_Sil6r
                                         ,"U2_ADAM17_Sil6r" = U2_ADAM17_Sil6r
                                         ,"ADAM17" = ADAM17
                                         ,"Toci" = Toci
                                         ,"Sil6r" = Sil6r
                                         ,"U_EGF_EGFR" = U_EGF_EGFR
                                         ,"EGF" = EGF
                                         ,"U_EGFR_TNF" = U_EGFR_TNF
                                         ,"TNF" = TNF
                                         ,"U_EGFR_IL6STAT3" = U_EGFR_IL6STAT3
                                         ,"Gefi" = Gefi
                                         ,"EGFR" = EGFR
                                         ,"U1_PRR_NFKB" = U1_PRR_NFKB
                                         ,"U2_PRR_NFKB" = U2_PRR_NFKB
                                         ,"PRR" = PRR
                                         ,"NFKB" = NFKB
                                         ,"IL6STAT3" = IL6STAT3
                                         ,"IL6AMP" = IL6AMP
                                         ,"cytok" = cytok)
  intv_data_list_egfr[[data_count]] <- interventional_data_egfr
  data_count = data_count + 1
}
#54 parameters in total
```

```{r}
#write.csv(intv_data_list[[1]], file = "data/Case3/obs_intv_data/intv_data1_Case3.csv")
```

# True Stan model in presence of latent variables

```{r}
model_str_covid <- "
    data {
        int D;
        vector[D] SARS_COV2;
        vector[D] ACE2;
        vector[D] Ang;
        vector[D] AGTR1;
        vector[D] ADAM17;
        vector[D] Toci;
        vector[D] Sil6r;
        vector[D] EGF;
        vector[D] TNF;
        vector[D] Gefi;
        vector[D] EGFR;
        vector[D] PRR;
        vector[D] NFKB;
        vector[D] IL6STAT3;
        vector[D] IL6AMP;
        int<lower=0,upper=1> cytok[D];
    }
    parameters {
       real<lower=0> mu_U1_SARS_Ang; 
       real<lower=0> sigma_U1_SARS_Ang;
       real<lower=0> mu_U2_SARS_Ang; 
       real<lower=0> sigma_U2_SARS_Ang;
       real beta0_U_SARS_AngToSARS_COV2;
       real<lower=0> beta_U1_SARS_AngToSARS_COV2;
       real<lower=0> beta_U2_SARS_AngToSARS_COV2;
       real<lower=10, upper=30> beta0_SARS_COV2ToACE2;
       real<upper=0> beta_SARS_COV2ToACE2;
       real<lower=10, upper=30> beta0_ACE2_and_U_SARS_Ang_ToAng;
       real<upper=0> beta_ACE2ToAng;
       real<lower=0> beta_U1_SARS_AngToAng;
       real<lower=0> beta_U2_SARS_AngToAng;
       real beta0_AngToAGTR1;
       real<lower=0> beta_AngToAGTR1;
       real<lower=0> mu_U1_ADAM17_Sil6r;
       real<lower=0> sigma_U1_ADAM17_Sil6r;
       real<lower=0> mu_U2_ADAM17_Sil6r;
       real<lower=0> sigma_U2_ADAM17_Sil6r;
       real beta0_AGTR1_UToADAM17;
       real<lower=0> beta_AGTR1ToADAM17;
       real<lower=0> beta_U1_ADAM17_Sil6rToADAM17;
       real<lower=0> beta_U2_ADAM17_Sil6rToADAM17;
       real<lower=0> mu_Toci;
       real<lower=0> sigma_Toci;
       real beta0_ADAM17_U_TociToSil6r;
       real<lower=0> beta_ADAM17ToSil6r;
       real<lower=0> beta_U1ToSil6r;
       real<lower=0> beta_U2ToSil6r;
       real<upper=0> beta_TociToSil6r;
       real<lower=0> mu_U_EGF_EGFR;
       real<lower=0> sigma_U_EGF_EGFR;
       real beta0_ADAM17_UToEGF;
       real<lower=0> beta_ADAM17ToEGF;
       real<lower=0> beta_UToEGF;
       real<lower=0> mu_U_EGFR_TNF;
       real<lower=0> sigma_U_EGFR_TNF;
       real beta0_ADAM17_UToTNF;
       real<lower=0> beta_ADAM17ToTNF;
       real<lower=0> beta_UToTNF;
       real<lower=0> mu_U_EGFR_IL6STAT3;
       real<lower=0> sigma_U_EGFR_IL6STAT3;
       real beta0_EGF_3U;
       real<lower=0> mu_Gefi;
       real<lower=0> sigma_Gefi;
       real<lower=0> beta_EGFToEGFR;
       real<lower=0> beta_U1ToEGFR;
       real<lower=0> beta_U2ToEGFR;
       real<lower=0> beta_U3ToEGFR;
       real<upper=0> beta_GefiToEGFR;
       real<lower=0> mu_U1_PRR_NFKB;
       real<lower=0> sigma_U1_PRR_NFKB;
       real<lower=0> mu_U2_PRR_NFKB;
       real<lower=0> sigma_U2_PRR_NFKB;
       real beta0_SARS_UPRR;
       real<lower=0> beta_SARS_COV2ToPRR;
       real<lower=0> beta_U1ToPRR;
       real<lower=0> beta_U2ToPRR;
       real beta0_PRR_U_EGFR_TNFToNFKB;
       real<lower=0> beta_PRRToNFKB;
       real<lower=0> beta_U1ToNFKB;
       real<lower=0> beta_U2ToNFKB;
       real<lower=0> beta_EGFRToNFKB;
       real<lower=0> beta_TNFToNFKB;
       real beta0_NFKB_IL6STSTToIL6STAT3;
       real<lower=0> beta_UToIL6STAT3;
       real<lower=0> beta_Sil6rToIL6STAT3;
       real beta0_NFKB_IL6STATToIL6AMP;
       real<lower=0> beta_NFKBToIL6AMP;
       real<lower=0> beta_IL6STAT3ToIL6AMP;
       real beta0_IL6AMPTocytok;
       real<lower=0> beta_IL6AMPTocytok;
       vector[D] U1_SARS_Ang;
       vector[D] U2_SARS_Ang;
       vector[D] U1_ADAM17_Sil6r;
       vector[D] U2_ADAM17_Sil6r;
       vector[D] U_EGF_EGFR;
       vector[D] U_EGFR_TNF;
       vector[D] U_EGFR_IL6STAT3;
       vector[D] U1_PRR_NFKB;
       vector[D] U2_PRR_NFKB;
    }
    transformed parameters {
      vector[D] SARS_COV2_loc;
      vector[D] ACE2_loc;
      vector[D] Ang_loc;
      vector[D] AGTR1_loc;
      vector[D] ADAM17_loc;
      vector[D] Sil6r_loc;
      vector[D] EGF_loc;
      vector[D] TNF_loc;
      vector[D] EGFR_loc;
      vector[D] PRR_loc;
      vector[D] NFKB_loc;
      vector[D] IL6STAT3_loc;
      vector[D] IL6AMP_loc;
      for (i in 1:D){
        SARS_COV2_loc[i] = 100 / (1 + exp(-beta0_U_SARS_AngToSARS_COV2 -U1_SARS_Ang[i] * beta_U1_SARS_AngToSARS_COV2 -U2_SARS_Ang[i] * beta_U2_SARS_AngToSARS_COV2));
        ACE2_loc[i] = beta0_SARS_COV2ToACE2 + SARS_COV2[i] * beta_SARS_COV2ToACE2;
        Ang_loc[i] = beta0_ACE2_and_U_SARS_Ang_ToAng + ACE2[i] * beta_ACE2ToAng + U1_SARS_Ang[i] * beta_U1_SARS_AngToAng+ U2_SARS_Ang[i] * beta_U2_SARS_AngToAng;
        AGTR1_loc[i] = 100 / (1 + exp(-beta0_AngToAGTR1 - Ang[i] * beta_AngToAGTR1));
        ADAM17_loc[i] = 100 / (1 + exp(-beta0_AGTR1_UToADAM17 - AGTR1[i] * beta_AGTR1ToADAM17 - U1_ADAM17_Sil6r[i] * beta_U1_ADAM17_Sil6rToADAM17 - U2_ADAM17_Sil6r[i] * beta_U2_ADAM17_Sil6rToADAM17));
        Sil6r_loc[i] = 100 / (1 + exp(-beta0_ADAM17_U_TociToSil6r - ADAM17[i] * beta_ADAM17ToSil6r - U1_ADAM17_Sil6r[i] * beta_U1ToSil6r  - U2_ADAM17_Sil6r[i] * beta_U2ToSil6r - Toci[i] * beta_TociToSil6r));
        EGF_loc[i] = 100 / (1 + exp(-beta0_ADAM17_UToEGF - ADAM17[i] * beta_ADAM17ToEGF - U_EGF_EGFR[i] * beta_UToEGF));
        TNF_loc[i] = 100 / (1 + exp(-beta0_ADAM17_UToTNF - ADAM17[i] * beta_ADAM17ToTNF - U_EGFR_TNF[i] * beta_UToTNF));
        EGFR_loc[i] = 100 / (1 + exp(-beta0_EGF_3U - EGF[i] * beta_EGFToEGFR - U_EGFR_IL6STAT3[i] * beta_U1ToEGFR - U_EGFR_TNF[i] * beta_U2ToEGFR  - U_EGF_EGFR[i] * beta_U3ToEGFR - Gefi[i] * beta_GefiToEGFR));
        PRR_loc[i] = 100 / (1 + exp(-beta0_SARS_UPRR - SARS_COV2[i] * beta_SARS_COV2ToPRR - U1_PRR_NFKB[i] * beta_U1ToPRR - U2_PRR_NFKB[i] * beta_U2ToPRR));
        NFKB_loc[i] = 100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR[i] * beta_PRRToNFKB - U1_PRR_NFKB[i] * beta_U1ToNFKB - U2_PRR_NFKB[i] * beta_U2ToNFKB- EGFR[i] * beta_EGFRToNFKB  - TNF[i] * beta_TNFToNFKB));
        IL6STAT3_loc[i] = 100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3[i] * beta_UToIL6STAT3 - Sil6r[i] * beta_Sil6rToIL6STAT3));
        IL6AMP_loc[i] = 100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB[i] * beta_NFKBToIL6AMP - IL6STAT3[i] * beta_IL6STAT3ToIL6AMP));
      }
    }
    model {
        mu_U1_SARS_Ang ~ normal(22, 1); 
        sigma_U1_SARS_Ang ~ normal(10, 1); 
        mu_U2_SARS_Ang ~ normal(22, 1); 
        sigma_U2_SARS_Ang ~ normal(10, 1);
        mu_U1_ADAM17_Sil6r ~ normal(25, 1);
        sigma_U1_ADAM17_Sil6r ~ normal(10, 1);
        mu_U2_ADAM17_Sil6r ~ normal(25, 1);
        sigma_U2_ADAM17_Sil6r ~ normal(10, 1);
        beta0_U_SARS_AngToSARS_COV2 ~ normal(0, 10);
        beta_U1_SARS_AngToSARS_COV2 ~ normal(0,10);
        beta_U2_SARS_AngToSARS_COV2 ~ normal(0,10);
        beta0_SARS_COV2ToACE2 ~ normal(20,10);
        beta_SARS_COV2ToACE2 ~ normal(0,10);
        beta0_ACE2_and_U_SARS_Ang_ToAng ~ normal(20,10);
        beta_ACE2ToAng ~ normal(0,10);
        beta_U1_SARS_AngToAng ~ normal(0,10);
        beta_U2_SARS_AngToAng ~ normal(0,10);
        beta0_AngToAGTR1 ~ normal(0,10);
        beta_AngToAGTR1 ~ normal(0,10);
        beta0_AGTR1_UToADAM17 ~ normal(0,10);
        beta_AGTR1ToADAM17 ~ normal(0,10);
        beta_U1_ADAM17_Sil6rToADAM17 ~ normal(0,10);
        beta_U2_ADAM17_Sil6rToADAM17 ~ normal(0,10);
        mu_Toci ~ normal(45, 1);
        sigma_Toci ~ normal(10, 1);
        beta0_ADAM17_U_TociToSil6r ~ normal(0, 10);
        beta_ADAM17ToSil6r ~ normal(0, 10);
        beta_U1ToSil6r ~ normal(0, 10);
        beta_U2ToSil6r ~ normal(0, 10);
        beta_TociToSil6r ~ normal(0, 10);
        mu_U_EGF_EGFR ~ normal(50,1);
        sigma_U_EGF_EGFR ~ normal(10,1);
        beta0_ADAM17_UToEGF ~ normal(0,10);
        beta_ADAM17ToEGF ~ normal(0,10);
        beta_UToEGF ~ normal(0,10);
        mu_U_EGFR_TNF ~ normal(45,1);
        sigma_U_EGFR_TNF ~ normal(10,1);
        beta0_ADAM17_UToTNF ~ normal(0, 10);
        beta_ADAM17ToTNF ~ normal(0, 10);
        beta_UToTNF ~ normal(0, 10);
        mu_U_EGFR_IL6STAT3 ~ normal(40,1);
        sigma_U_EGFR_IL6STAT3 ~ normal(10,1);
        beta0_EGF_3U ~ normal(0, 10);
        mu_Gefi ~ normal(40,1);
        sigma_Gefi ~ normal(10,1);
        beta_EGFToEGFR ~ normal(0, 10);
        beta_U1ToEGFR ~ normal(0, 10);
        beta_U2ToEGFR ~ normal(0, 10);
        beta_U3ToEGFR ~ normal(0, 10); 
        beta_GefiToEGFR ~ normal(0,10);
        mu_U1_PRR_NFKB ~ normal(20, 1);
        sigma_U1_PRR_NFKB ~ normal(10,1);
        mu_U2_PRR_NFKB ~ normal(20, 1);
        sigma_U2_PRR_NFKB ~ normal(10,1);
        beta0_SARS_UPRR ~ normal(0, 10);
        beta_SARS_COV2ToPRR ~ normal(0, 10);
        beta_U1ToPRR ~ normal(0, 10);
        beta_U2ToPRR ~ normal(0, 10);
        beta_PRRToNFKB ~ normal(0, 10);
        beta_U1ToNFKB ~ normal(0, 10);
        beta_U2ToNFKB ~ normal(0, 10);
        beta_EGFRToNFKB ~ normal(0, 10);
        beta_TNFToNFKB ~ normal(0, 10);
        beta0_NFKB_IL6STSTToIL6STAT3 ~ normal(0, 10);
        beta_UToIL6STAT3 ~ normal(0, 10);
        beta_Sil6rToIL6STAT3 ~ normal(0, 10);
        beta0_NFKB_IL6STATToIL6AMP ~ normal(0, 10);
        beta_NFKBToIL6AMP ~ normal(0, 10);
        beta_IL6STAT3ToIL6AMP ~ normal(0, 10); 
        beta0_IL6AMPTocytok ~ normal(0, 10);
        beta_IL6AMPTocytok ~ normal(0, 10);         
        //
        U1_SARS_Ang ~ normal(mu_U1_SARS_Ang, sigma_U1_SARS_Ang);      // likelihood
        U2_SARS_Ang ~ normal(mu_U2_SARS_Ang, sigma_U2_SARS_Ang);
        SARS_COV2 ~ normal(SARS_COV2_loc, 101);
        ACE2 ~ normal(ACE2_loc,1.6);
        Ang ~ normal(Ang_loc,6);
        AGTR1 ~ normal(AGTR1_loc,7.6);
        ADAM17 ~ normal(ADAM17_loc,8.7);
        U1_ADAM17_Sil6r ~ normal(mu_U1_ADAM17_Sil6r, sigma_U1_ADAM17_Sil6r);
        U2_ADAM17_Sil6r ~ normal(mu_U2_ADAM17_Sil6r, sigma_U2_ADAM17_Sil6r);
        Toci ~ normal(mu_Toci, sigma_Toci);
        Sil6r ~ normal(Sil6r_loc,17.9);
        U_EGF_EGFR ~ normal(mu_U_EGF_EGFR, sigma_U_EGF_EGFR);
        EGF ~ normal(EGF_loc,7);
        U_EGFR_TNF ~ normal(mu_U_EGFR_TNF,sigma_U_EGFR_TNF);
        TNF ~ normal(TNF_loc, 6.5);
        U_EGFR_IL6STAT3 ~ normal(mu_U_EGFR_IL6STAT3, sigma_U_EGFR_IL6STAT3);
        EGFR ~ normal(EGFR_loc, 13.3);
        U1_PRR_NFKB ~ normal(mu_U1_PRR_NFKB,sigma_U1_PRR_NFKB);
        U2_PRR_NFKB ~ normal(mu_U2_PRR_NFKB,sigma_U2_PRR_NFKB);
        PRR ~ normal(PRR_loc,14.1);
        NFKB ~ normal(NFKB_loc,10);
        IL6STAT3 ~ normal(IL6STAT3_loc, 18.6);
        IL6AMP ~ normal(IL6AMP_loc, 12);
        for(i in 1:D) {
        cytok[i] ~ bernoulli_logit(beta0_IL6AMPTocytok + IL6AMP[i] * beta_IL6AMPTocytok);
        }
    }
"
```


```{r, message=FALSE, warning=FALSE}
mod <- rstan::stan_model(model_code = model_str_covid)
```

```{r}
hmc_fit_list <- rep(list(list()), K)

start_time <- Sys.time()

for (num_data_points in ndp) {
  print("num_data_points is:")
  print(num_data_points)
  for (data_count in 1:K) {
    print("data_count is:")
    print(data_count)
    data_list <- list(D=num_data_points
                  ,SARS_COV2 = obs_data_list[[data_count]]$SARS_COV2[1:num_data_points]
                  ,ACE2 = obs_data_list[[data_count]]$ACE2[1:num_data_points]
                  ,Ang = obs_data_list[[data_count]]$Ang[1:num_data_points]
                  ,AGTR1 = obs_data_list[[data_count]]$AGTR1[1:num_data_points]
                  ,ADAM17 = obs_data_list[[data_count]]$ADAM17[1:num_data_points]
                  ,Toci = obs_data_list[[data_count]]$Toci[1:num_data_points]
                  ,Sil6r = obs_data_list[[data_count]]$Sil6r[1:num_data_points]
                  ,EGF = obs_data_list[[data_count]]$EGF[1:num_data_points]
                  ,TNF = obs_data_list[[data_count]]$TNF[1:num_data_points]
                  ,Gefi = obs_data_list[[data_count]]$Gefi[1:num_data_points]
                  ,EGFR = obs_data_list[[data_count]]$EGFR[1:num_data_points]
                  ,PRR = obs_data_list[[data_count]]$PRR[1:num_data_points]
                  ,NFKB = obs_data_list[[data_count]]$NFKB[1:num_data_points]
                  ,IL6STAT3= obs_data_list[[data_count]]$IL6STAT3[1:num_data_points]
                  ,IL6AMP = obs_data_list[[data_count]]$IL6AMP[1:num_data_points]
                  ,cytok = obs_data_list[[data_count]]$cytok[1:num_data_points])
    
    hmc_fit_list[[data_count]][[paste0("num_data_points_",num_data_points)]] <- rstan::sampling(mod, data=data_list, chains = 2, iter = 3000, warmup = 1500, seed = 1, control = list(max_treedepth = 15))
    
  }
}
end_time <- Sys.time()
end_time - start_time
#14 hours for ndp=60 #20 hours for ndp = 100 #20 hours for ndp = 200
#saveRDS(hmc_fit_list,file = "hmc_fit_list_Case3.RData")
```


## Mutilated model

```{r}
num_samples = 1000
mutilated_model_sil6r <- function(mu_U1_SARS_Ang, sigma_U1_SARS_Ang,mu_U2_SARS_Ang, sigma_U2_SARS_Ang
                            ,beta0_U_SARS_AngToSARS_COV2,beta_U1_SARS_AngToSARS_COV2,beta_U2_SARS_AngToSARS_COV2
                            ,beta0_SARS_COV2ToACE2, beta_SARS_COV2ToACE2
                            ,beta0_ACE2_and_U_SARS_Ang_ToAng, beta_ACE2ToAng, beta_U1_SARS_AngToAng, beta_U2_SARS_AngToAng
                            ,beta0_AngToAGTR1, beta_AngToAGTR1
                            ,mu_U1_ADAM17_Sil6r,sigma_U1_ADAM17_Sil6r,mu_U2_ADAM17_Sil6r,sigma_U2_ADAM17_Sil6r
                            ,beta0_AGTR1_UToADAM17,beta_AGTR1ToADAM17, beta_U1_ADAM17_Sil6rToADAM17,beta_U2_ADAM17_Sil6rToADAM17
                            ,mu_Toci, sigma_Toci
                            ,beta0_ADAM17_U_TociToSil6r, beta_ADAM17ToSil6r, beta_U1ToSil6r, beta_U2ToSil6r, beta_TociToSil6r
                            ,mu_U_EGF_EGFR, sigma_U_EGF_EGFR
                            ,beta0_ADAM17_UToEGF, beta_ADAM17ToEGF, beta_UToEGF
                            ,mu_U_EGFR_TNF, sigma_U_EGFR_TNF
                            ,beta0_ADAM17_UToTNF, beta_ADAM17ToTNF, beta_UToTNF
                            ,mu_U_EGFR_IL6STAT3,sigma_U_EGFR_IL6STAT3
                            ,beta0_EGF_3U, beta_EGFToEGFR, beta_U1ToEGFR, beta_U2ToEGFR, beta_U3ToEGFR, beta_GefiToEGFR
                            ,mu_U1_PRR_NFKB, sigma_U1_PRR_NFKB, mu_U2_PRR_NFKB, sigma_U2_PRR_NFKB
                            ,beta0_SARS_UPRR, beta_SARS_COV2ToPRR, beta_U1ToPRR, beta_U2ToPRR
                            ,beta0_PRR_U_EGFR_TNFToNFKB, beta_PRRToNFKB, beta_U1ToNFKB, beta_U2ToNFKB, beta_EGFRToNFKB, beta_TNFToNFKB
                            ,beta0_NFKB_IL6STSTToIL6STAT3, beta_UToIL6STAT3, beta_Sil6rToIL6STAT3
                            ,beta0_NFKB_IL6STATToIL6AMP, beta_NFKBToIL6AMP, beta_IL6STAT3ToIL6AMP
                            ,beta0_IL6AMPTocytok, beta_IL6AMPTocytok,
                            mu_Gefi, sigma_Gefi,
                            seed, data_count
) {
    set.seed(seed)
    U1_SARS_Ang_1 <- rnorm(num_samples, mu_U1_SARS_Ang, sigma_U1_SARS_Ang)
    U2_SARS_Ang_1 <- rnorm(num_samples, mu_U2_SARS_Ang, sigma_U2_SARS_Ang)
    SARS_COV2_1 = #rnorm(num_samples,
                        100 / (1 + exp(-beta0_U_SARS_AngToSARS_COV2 - U1_SARS_Ang_1 * beta_U1_SARS_AngToSARS_COV2 - U2_SARS_Ang_1 * beta_U2_SARS_AngToSARS_COV2))#,
                        #sqrt(var(obs_data_list[[data_count]]$SARS_COV2))
                        #)
    ACE2_1 = #rnorm(num_samples,
                   beta0_SARS_COV2ToACE2 + SARS_COV2_1 * beta_SARS_COV2ToACE2#,
                   #sqrt(var(obs_data_list[[data_count]]$ACE2))
                   #)
    Ang_1 = #rnorm(num_samples,
                  beta0_ACE2_and_U_SARS_Ang_ToAng + ACE2_1 * beta_ACE2ToAng + U1_SARS_Ang_1 *beta_U1_SARS_AngToAng + U2_SARS_Ang_1 *beta_U2_SARS_AngToAng#,
                  #sqrt(var(obs_data_list[[data_count]]$Ang))
                  #)
    AGTR1_1 = #rnorm(num_samples,
                    100 / (1 + exp(-beta0_AngToAGTR1 - Ang_1 * beta_AngToAGTR1))#,
                    #sqrt(var(obs_data_list[[data_count]]$AGTR1))
                    #)
    U1_ADAM17_Sil6r_1 = rnorm(num_samples,mu_U1_ADAM17_Sil6r,sigma_U1_ADAM17_Sil6r)
    U2_ADAM17_Sil6r_1 = rnorm(num_samples,mu_U2_ADAM17_Sil6r,sigma_U2_ADAM17_Sil6r)
    ADAM17_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_AGTR1_UToADAM17 - AGTR1_1 * beta_AGTR1ToADAM17 - U1_ADAM17_Sil6r_1 * beta_U1_ADAM17_Sil6rToADAM17 - U2_ADAM17_Sil6r_1 * beta_U2_ADAM17_Sil6rToADAM17))#,
                     #sqrt(var(obs_data_list[[data_count]]$ADAM17))
                     #)
    Toci_1 = rnorm(num_samples,mu_Toci, sigma_Toci)
    
    Sil6r_1 = rep(20, num_samples)
    
    U_EGF_EGFR_1 = rnorm(num_samples, mu_U_EGF_EGFR, sigma_U_EGF_EGFR)
    EGF_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_UToEGF - ADAM17_1 * beta_ADAM17ToEGF - U_EGF_EGFR_1 * beta_UToEGF))#,
                  #sqrt(var(obs_data_list[[data_count]]$EGF))
                  #)
    U_EGFR_TNF_1 = rnorm(num_samples, mu_U_EGFR_TNF, sigma_U_EGFR_TNF)
    TNF_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_UToTNF - ADAM17_1 * beta_ADAM17ToTNF - U_EGFR_TNF_1 * beta_UToTNF))# ,
                  #sqrt(var(obs_data_list[[data_count]]$TNF))
                  #)
    U_EGFR_IL6STAT3_1 =  rnorm(num_samples, mu_U_EGFR_IL6STAT3, sigma_U_EGFR_IL6STAT3)
    Gefi_1 = rnorm(num_samples, mu_Gefi, sigma_Gefi)
    EGFR_1 = #rnorm(num_samples,
                   100 / (1 + exp(-beta0_EGF_3U - EGF_1 * beta_EGFToEGFR - U_EGFR_IL6STAT3_1 * beta_U1ToEGFR - U_EGFR_TNF_1 * beta_U2ToEGFR  - U_EGF_EGFR_1 * beta_U3ToEGFR - Gefi_1 * beta_GefiToEGFR))#,
                   #sqrt(var(obs_data_list[[data_count]]$EGFR))
                   #)
    U1_PRR_NFKB_1 = rnorm(num_samples, mu_U1_PRR_NFKB, sigma_U1_PRR_NFKB)
    U2_PRR_NFKB_1 = rnorm(num_samples, mu_U2_PRR_NFKB, sigma_U2_PRR_NFKB)
    PRR_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_SARS_UPRR - SARS_COV2_1 * beta_SARS_COV2ToPRR - U1_PRR_NFKB_1 * beta_U1ToPRR - U2_PRR_NFKB_1 * beta_U2ToPRR))# ,
                  #sqrt(var(obs_data_list[[data_count]]$PRR))
                  #)
    NFKB_1 = #rnorm(num_samples,
                   100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR_1 * beta_PRRToNFKB - U1_PRR_NFKB_1 * beta_U1ToNFKB  - U2_PRR_NFKB_1 * beta_U2ToNFKB- EGFR_1 * beta_EGFRToNFKB  - TNF_1 * beta_TNFToNFKB))# ,
                   #sqrt(var(obs_data_list[[data_count]]$NFKB))
                   #)
    IL6STAT3_1 = #rnorm(num_samples,
                       100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3_1 * beta_UToIL6STAT3 - Sil6r_1 * beta_Sil6rToIL6STAT3))#,
                       #sqrt(var(obs_data_list[[data_count]]$IL6STAT3))
                       #)
    IL6AMP_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB_1 * beta_NFKBToIL6AMP - IL6STAT3_1 * beta_IL6STAT3ToIL6AMP))#,
                     #sqrt(var(obs_data_list[[data_count]]$IL6AMP))
                     #)
    p_cytok = 1 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP_1 * beta_IL6AMPTocytok))
    cytok_1 = rbinom(n = num_samples, size = 1, prob = p_cytok)
    return(cytok_1)
}
```

```{r}
num_samples = 1000
mutilated_model_egfr <- function(mu_U1_SARS_Ang, sigma_U1_SARS_Ang,mu_U2_SARS_Ang, sigma_U2_SARS_Ang
                            ,beta0_U_SARS_AngToSARS_COV2,beta_U1_SARS_AngToSARS_COV2,beta_U2_SARS_AngToSARS_COV2
                            ,beta0_SARS_COV2ToACE2, beta_SARS_COV2ToACE2
                            ,beta0_ACE2_and_U_SARS_Ang_ToAng, beta_ACE2ToAng, beta_U1_SARS_AngToAng, beta_U2_SARS_AngToAng
                            ,beta0_AngToAGTR1, beta_AngToAGTR1
                            ,mu_U1_ADAM17_Sil6r,sigma_U1_ADAM17_Sil6r,mu_U2_ADAM17_Sil6r,sigma_U2_ADAM17_Sil6r
                            ,beta0_AGTR1_UToADAM17,beta_AGTR1ToADAM17, beta_U1_ADAM17_Sil6rToADAM17,beta_U2_ADAM17_Sil6rToADAM17
                            ,mu_Toci, sigma_Toci
                            ,beta0_ADAM17_U_TociToSil6r, beta_ADAM17ToSil6r, beta_U1ToSil6r, beta_U2ToSil6r, beta_TociToSil6r
                            ,mu_U_EGF_EGFR, sigma_U_EGF_EGFR
                            ,beta0_ADAM17_UToEGF, beta_ADAM17ToEGF, beta_UToEGF
                            ,mu_U_EGFR_TNF, sigma_U_EGFR_TNF
                            ,beta0_ADAM17_UToTNF, beta_ADAM17ToTNF, beta_UToTNF
                            ,mu_U_EGFR_IL6STAT3,sigma_U_EGFR_IL6STAT3
                            ,beta0_EGF_3U, beta_EGFToEGFR, beta_U1ToEGFR, beta_U2ToEGFR, beta_U3ToEGFR, beta_GefiToEGFR
                            ,mu_U1_PRR_NFKB, sigma_U1_PRR_NFKB, mu_U2_PRR_NFKB, sigma_U2_PRR_NFKB
                            ,beta0_SARS_UPRR, beta_SARS_COV2ToPRR, beta_U1ToPRR, beta_U2ToPRR
                            ,beta0_PRR_U_EGFR_TNFToNFKB, beta_PRRToNFKB, beta_U1ToNFKB, beta_U2ToNFKB, beta_EGFRToNFKB, beta_TNFToNFKB
                            ,beta0_NFKB_IL6STSTToIL6STAT3, beta_UToIL6STAT3, beta_Sil6rToIL6STAT3
                            ,beta0_NFKB_IL6STATToIL6AMP, beta_NFKBToIL6AMP, beta_IL6STAT3ToIL6AMP
                            ,beta0_IL6AMPTocytok, beta_IL6AMPTocytok,
                            mu_Gefi, sigma_Gefi,
                            seed, data_count
) {
    set.seed(seed)
    U1_SARS_Ang_1 <- rnorm(num_samples, mu_U1_SARS_Ang, sigma_U1_SARS_Ang)
    U2_SARS_Ang_1 <- rnorm(num_samples, mu_U2_SARS_Ang, sigma_U2_SARS_Ang)
    SARS_COV2_1 = #rnorm(num_samples,
                        100 / (1 + exp(-beta0_U_SARS_AngToSARS_COV2 - U1_SARS_Ang_1 * beta_U1_SARS_AngToSARS_COV2 - U2_SARS_Ang_1 * beta_U2_SARS_AngToSARS_COV2))#,
                        #sqrt(var(obs_data_list[[data_count]]$SARS_COV2))
                        #)
    ACE2_1 = #rnorm(num_samples,
                   beta0_SARS_COV2ToACE2 + SARS_COV2_1 * beta_SARS_COV2ToACE2#,
                   #sqrt(var(obs_data_list[[data_count]]$ACE2))
                   #)
    Ang_1 = #rnorm(num_samples,
                  beta0_ACE2_and_U_SARS_Ang_ToAng + ACE2_1 * beta_ACE2ToAng + U1_SARS_Ang_1 *beta_U1_SARS_AngToAng + U2_SARS_Ang_1 *beta_U2_SARS_AngToAng#,
                  #sqrt(var(obs_data_list[[data_count]]$Ang))
                  #)
    AGTR1_1 = #rnorm(num_samples,
                    100 / (1 + exp(-beta0_AngToAGTR1 - Ang_1 * beta_AngToAGTR1))#,
                    #sqrt(var(obs_data_list[[data_count]]$AGTR1))
                    #)
    U1_ADAM17_Sil6r_1 = rnorm(num_samples,mu_U1_ADAM17_Sil6r,sigma_U1_ADAM17_Sil6r)
    U2_ADAM17_Sil6r_1 = rnorm(num_samples,mu_U2_ADAM17_Sil6r,sigma_U2_ADAM17_Sil6r)
    ADAM17_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_AGTR1_UToADAM17 - AGTR1_1 * beta_AGTR1ToADAM17 - U1_ADAM17_Sil6r_1 * beta_U1_ADAM17_Sil6rToADAM17 - U2_ADAM17_Sil6r_1 * beta_U2_ADAM17_Sil6rToADAM17))#,
                     #sqrt(var(obs_data_list[[data_count]]$ADAM17))
                     #)
    Toci_1 = rnorm(num_samples,mu_Toci, sigma_Toci)
    
    Sil6r_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_U_TociToSil6r - ADAM17_1 * beta_ADAM17ToSil6r - U1_ADAM17_Sil6r_1 * beta_U1ToSil6r  - U2_ADAM17_Sil6r_1 * beta_U2ToSil6r - Toci_1 * beta_TociToSil6r))#,
                  #sqrt(var(obs_data_list[[data_count]]$EGF))
                  #)
    
    U_EGF_EGFR_1 = rnorm(num_samples, mu_U_EGF_EGFR, sigma_U_EGF_EGFR)
    EGF_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_UToEGF - ADAM17_1 * beta_ADAM17ToEGF - U_EGF_EGFR_1 * beta_UToEGF))#,
                  #sqrt(var(obs_data_list[[data_count]]$EGF))
                  #)
    U_EGFR_TNF_1 = rnorm(num_samples, mu_U_EGFR_TNF, sigma_U_EGFR_TNF)
    TNF_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_UToTNF - ADAM17_1 * beta_ADAM17ToTNF - U_EGFR_TNF_1 * beta_UToTNF))# ,
                  #sqrt(var(obs_data_list[[data_count]]$TNF))
                  #)
    U_EGFR_IL6STAT3_1 =  rnorm(num_samples, mu_U_EGFR_IL6STAT3, sigma_U_EGFR_IL6STAT3)
    Gefi_1 = rnorm(num_samples, mu_Gefi, sigma_Gefi)
    EGFR_1 = rep(20, num_samples)
    U1_PRR_NFKB_1 = rnorm(num_samples, mu_U1_PRR_NFKB, sigma_U1_PRR_NFKB)
    U2_PRR_NFKB_1 = rnorm(num_samples, mu_U2_PRR_NFKB, sigma_U2_PRR_NFKB)
    PRR_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_SARS_UPRR - SARS_COV2_1 * beta_SARS_COV2ToPRR - U1_PRR_NFKB_1 * beta_U1ToPRR - U2_PRR_NFKB_1 * beta_U2ToPRR))# ,
                  #sqrt(var(obs_data_list[[data_count]]$PRR))
                  #)
    NFKB_1 = #rnorm(num_samples,
                   100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR_1 * beta_PRRToNFKB - U1_PRR_NFKB_1 * beta_U1ToNFKB  - U2_PRR_NFKB_1 * beta_U2ToNFKB- EGFR_1 * beta_EGFRToNFKB  - TNF_1 * beta_TNFToNFKB))# ,
                   #sqrt(var(obs_data_list[[data_count]]$NFKB))
                   #)
    IL6STAT3_1 = #rnorm(num_samples,
                       100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3_1 * beta_UToIL6STAT3 - Sil6r_1 * beta_Sil6rToIL6STAT3))#,
                       #sqrt(var(obs_data_list[[data_count]]$IL6STAT3))
                       #)
    IL6AMP_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB_1 * beta_NFKBToIL6AMP - IL6STAT3_1 * beta_IL6STAT3ToIL6AMP))#,
                     #sqrt(var(obs_data_list[[data_count]]$IL6AMP))
                     #)
    p_cytok = 1 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP_1 * beta_IL6AMPTocytok))
    cytok_1 = rbinom(n = num_samples, size = 1, prob = p_cytok)
    return(cytok_1)
}
```

This is the whole parametes for this case study:

```{r}
parameters <- c("mu_U1_SARS_Ang", "sigma_U1_SARS_Ang", "mu_U2_SARS_Ang", "sigma_U2_SARS_Ang"
                                     ,"beta0_U_SARS_AngToSARS_COV2","beta_U1_SARS_AngToSARS_COV2","beta_U2_SARS_AngToSARS_COV2"
                                     ,"beta0_SARS_COV2ToACE2", "beta_SARS_COV2ToACE2"
                                     ,"beta0_ACE2_and_U_SARS_Ang_ToAng", "beta_ACE2ToAng", "beta_U1_SARS_AngToAng","beta_U2_SARS_AngToAng"
                                     ,"beta0_AngToAGTR1", "beta_AngToAGTR1"
                                     ,"mu_U1_ADAM17_Sil6r", "sigma_U1_ADAM17_Sil6r","mu_U2_ADAM17_Sil6r", "sigma_U2_ADAM17_Sil6r"
                                     ,"beta0_AGTR1_UToADAM17", "beta_AGTR1ToADAM17","beta_U1_ADAM17_Sil6rToADAM17","beta_U2_ADAM17_Sil6rToADAM17"
                                     ,"mu_Toci", "sigma_Toci"
                                     ,"beta0_ADAM17_U_TociToSil6r", "beta_ADAM17ToSil6r", "beta_U1ToSil6r", "beta_U2ToSil6r", "beta_TociToSil6r"
                                     ,"mu_U_EGF_EGFR", "sigma_U_EGF_EGFR"
                                     ,"beta0_ADAM17_UToEGF", "beta_ADAM17ToEGF", "beta_UToEGF"
                                     ,"mu_U_EGFR_TNF", "sigma_U_EGFR_TNF"
                                     ,"beta0_ADAM17_UToTNF", "beta_ADAM17ToTNF", "beta_UToTNF"
                                     ,"mu_U_EGFR_IL6STAT3", "sigma_U_EGFR_IL6STAT3"
                                     ,"beta0_EGF_3U", "beta_EGFToEGFR", "beta_U1ToEGFR", "beta_U2ToEGFR", "beta_U3ToEGFR", "beta_GefiToEGFR"
                                     ,"mu_U1_PRR_NFKB", "sigma_U1_PRR_NFKB","mu_U2_PRR_NFKB", "sigma_U2_PRR_NFKB"
                                     ,"beta0_SARS_UPRR", "beta_SARS_COV2ToPRR", "beta_U1ToPRR", "beta_U2ToPRR"
                                     ,"beta0_PRR_U_EGFR_TNFToNFKB", "beta_PRRToNFKB", "beta_U1ToNFKB", "beta_U2ToNFKB", "beta_EGFRToNFKB", "beta_TNFToNFKB"  
                                     ,"beta0_NFKB_IL6STSTToIL6STAT3", "beta_UToIL6STAT3", "beta_Sil6rToIL6STAT3"
                                     ,"beta0_NFKB_IL6STATToIL6AMP", "beta_NFKBToIL6AMP", "beta_IL6STAT3ToIL6AMP"
                                     ,"beta0_IL6AMPTocytok", "beta_IL6AMPTocytok",
                "mu_Gefi", "sigma_Gefi")

```


```{r}
#hmc_fit_list <- readRDS(file = "data/Case3_Covid/output/hmc_fit_list_Case3.RData")
estimated_y_hmc_list <- rep(list(list()), K)
means_hmc <- c()
means_hmc_list <- list()
seed = 5
for (num_data_points in ndp) {
  for (data_count in 1:K) {
    samples_hmc <- rstan::extract(hmc_fit_list[[data_count]][[paste0("num_data_points_",num_data_points)]], parameters)
    estimated_y_hmc_list[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model_sil6r(mu_U1_SARS_Ang = mean(samples_hmc$mu_U1_SARS_Ang),
                                                           sigma_U1_SARS_Ang = mean(samples_hmc$sigma_U1_SARS_Ang),
                                                           mu_U2_SARS_Ang = mean(samples_hmc$mu_U2_SARS_Ang),
                                                           sigma_U2_SARS_Ang = mean(samples_hmc$sigma_U2_SARS_Ang),
                                                           beta0_U_SARS_AngToSARS_COV2 = mean(samples_hmc$beta0_U_SARS_AngToSARS_COV2),
                                                           beta_U1_SARS_AngToSARS_COV2 = mean(samples_hmc$beta_U1_SARS_AngToSARS_COV2),
                                                           beta_U2_SARS_AngToSARS_COV2 = mean(samples_hmc$beta_U2_SARS_AngToSARS_COV2),
                                                           beta0_SARS_COV2ToACE2 = mean(samples_hmc$beta0_SARS_COV2ToACE2),
                                                           beta_SARS_COV2ToACE2 = mean(samples_hmc$beta_SARS_COV2ToACE2),
                                                           beta0_ACE2_and_U_SARS_Ang_ToAng = mean(samples_hmc$beta0_ACE2_and_U_SARS_Ang_ToAng),
                                                           beta_ACE2ToAng = mean(samples_hmc$beta_ACE2ToAng),
                                                           beta_U1_SARS_AngToAng = mean(samples_hmc$beta_U1_SARS_AngToAng),
                                                           beta_U2_SARS_AngToAng = mean(samples_hmc$beta_U2_SARS_AngToAng),
                                                           beta0_AngToAGTR1 = mean(samples_hmc$beta0_AngToAGTR1),
                                                           beta_AngToAGTR1 = mean(samples_hmc$beta_AngToAGTR1),
                                                           mu_U1_ADAM17_Sil6r = mean(samples_hmc$mu_U1_ADAM17_Sil6r),
                                                           sigma_U1_ADAM17_Sil6r = mean(samples_hmc$sigma_U1_ADAM17_Sil6r),
                                                           mu_U2_ADAM17_Sil6r = mean(samples_hmc$mu_U2_ADAM17_Sil6r),
                                                           sigma_U2_ADAM17_Sil6r = mean(samples_hmc$sigma_U2_ADAM17_Sil6r),
                                                           beta0_AGTR1_UToADAM17 = mean(samples_hmc$beta0_AGTR1_UToADAM17),
                                                           beta_AGTR1ToADAM17 = mean(samples_hmc$beta_AGTR1ToADAM17),
                                                           beta_U1_ADAM17_Sil6rToADAM17 = mean(samples_hmc$beta_U1_ADAM17_Sil6rToADAM17),
                                                           beta_U2_ADAM17_Sil6rToADAM17 = mean(samples_hmc$beta_U2_ADAM17_Sil6rToADAM17),
                                                           mu_Toci = mean(samples_hmc$mu_Toci),
                                                           sigma_Toci = mean(samples_hmc$sigma_Toci),
                                                           beta0_ADAM17_U_TociToSil6r = mean(samples_hmc$beta0_ADAM17_U_TociToSil6r),
                                                           beta_ADAM17ToSil6r = mean(samples_hmc$beta_ADAM17ToSil6r),
                                                           beta_U1ToSil6r = mean(samples_hmc$beta_U1ToSil6r),
                                                           beta_U2ToSil6r = mean(samples_hmc$beta_U2ToSil6r),
                                                           beta_TociToSil6r = mean(samples_hmc$beta_TociToSil6r),
                                                           mu_U_EGF_EGFR = mean(samples_hmc$mu_U_EGF_EGFR),
                                                           sigma_U_EGF_EGFR = mean(samples_hmc$sigma_U_EGF_EGFR),
                                                           beta0_ADAM17_UToEGF = mean(samples_hmc$beta0_ADAM17_UToEGF),
                                                           beta_ADAM17ToEGF = mean(samples_hmc$beta_ADAM17ToEGF),
                                                           beta_UToEGF = mean(samples_hmc$beta_UToEGF),
                                                           mu_U_EGFR_TNF = mean(samples_hmc$mu_U_EGFR_TNF),
                                                           sigma_U_EGFR_TNF = mean(samples_hmc$sigma_U_EGFR_TNF),
                                                           beta0_ADAM17_UToTNF = mean(samples_hmc$beta0_ADAM17_UToTNF),
                                                           beta_ADAM17ToTNF = mean(samples_hmc$beta_ADAM17ToTNF),
                                                           beta_UToTNF = mean(samples_hmc$beta_UToTNF),
                                                           mu_U_EGFR_IL6STAT3 = mean(samples_hmc$mu_U_EGFR_IL6STAT3),
                                                           sigma_U_EGFR_IL6STAT3 = mean(samples_hmc$sigma_U_EGFR_IL6STAT3),
                                                           beta0_EGF_3U = mean(samples_hmc$beta0_EGF_3U),
                                                           beta_EGFToEGFR = mean(samples_hmc$beta_EGFToEGFR),
                                                           beta_U1ToEGFR = mean(samples_hmc$beta_U1ToEGFR),
                                                           beta_U2ToEGFR = mean(samples_hmc$beta_U2ToEGFR),
                                                           beta_U3ToEGFR = mean(samples_hmc$beta_U3ToEGFR),
                                                           beta_GefiToEGFR = mean(samples_hmc$beta_GefiToEGFR),
                                                           mu_U1_PRR_NFKB = mean(samples_hmc$mu_U1_PRR_NFKB),
                                                           sigma_U1_PRR_NFKB = mean(samples_hmc$sigma_U1_PRR_NFKB),
                                                           mu_U2_PRR_NFKB = mean(samples_hmc$mu_U2_PRR_NFKB),
                                                           sigma_U2_PRR_NFKB = mean(samples_hmc$sigma_U2_PRR_NFKB),
                                                           beta0_SARS_UPRR = mean(samples_hmc$beta0_SARS_UPRR),
                                                           beta_SARS_COV2ToPRR = mean(samples_hmc$beta_SARS_COV2ToPRR),
                                                           beta_U1ToPRR = mean(samples_hmc$beta_U1ToPRR),
                                                           beta_U2ToPRR = mean(samples_hmc$beta_U2ToPRR),
                                                           beta0_PRR_U_EGFR_TNFToNFKB = mean(samples_hmc$beta0_PRR_U_EGFR_TNFToNFKB),
                                                           beta_PRRToNFKB = mean(samples_hmc$beta_PRRToNFKB),
                                                           beta_U1ToNFKB = mean(samples_hmc$beta_U1ToNFKB),
                                                           beta_U2ToNFKB = mean(samples_hmc$beta_U2ToNFKB),
                                                           beta_EGFRToNFKB = mean(samples_hmc$beta_EGFRToNFKB),
                                                           beta_TNFToNFKB = mean(samples_hmc$beta_TNFToNFKB),
                                                           beta0_NFKB_IL6STSTToIL6STAT3 = mean(samples_hmc$beta0_NFKB_IL6STSTToIL6STAT3),
                                                           beta_UToIL6STAT3 = mean(samples_hmc$beta_UToIL6STAT3),
                                                           beta_Sil6rToIL6STAT3 = mean(samples_hmc$beta_Sil6rToIL6STAT3),
                                                           beta0_NFKB_IL6STATToIL6AMP = mean(samples_hmc$beta0_NFKB_IL6STATToIL6AMP),
                                                           beta_NFKBToIL6AMP = mean(samples_hmc$beta_NFKBToIL6AMP),
                                                           beta_IL6STAT3ToIL6AMP = mean(samples_hmc$beta_IL6STAT3ToIL6AMP),
                                                           beta0_IL6AMPTocytok= mean(samples_hmc$beta0_IL6AMPTocytok),
                                                           beta_IL6AMPTocytok = mean(samples_hmc$beta_IL6AMPTocytok),
                                                           mu_Gefi = mean(samples_hmc$mu_Gefi),
                                                           sigma_Gefi = mean(samples_hmc$sigma_Gefi),
                                                           seed = seed,
                                                           data_count = data_count
    )
    means_hmc <- c(means_hmc,abs(mean(estimated_y_hmc_list[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list_sil6r[[data_count]]$cytok)))
  }
  means_hmc_list[[paste0("num_data_points_",num_data_points)]] <- means_hmc
  means_hmc <- c()
}
saveRDS(means_hmc_list,file = "data/Case3_Covid/output/means_hmc_list_Case3_sil6r.RData")
```


```{r}
hmc_fit_list <- readRDS(file = "data/Case3_Covid/output/hmc_fit_list_Case3.RData")
estimated_y_hmc_list <- rep(list(list()), K)
means_hmc <- c()
means_hmc_list <- list()
seed = 5

start_time <- Sys.time()

for (num_data_points in ndp) {
  for (data_count in 1:K) {

    samples_hmc <- rstan::extract(hmc_fit_list[[data_count]][[paste0("num_data_points_",num_data_points)]], parameters)
    
    estimated_y_hmc_list[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model_egfr(mu_U1_SARS_Ang = mean(samples_hmc$mu_U1_SARS_Ang),
                                                           sigma_U1_SARS_Ang = mean(samples_hmc$sigma_U1_SARS_Ang),
                                                           mu_U2_SARS_Ang = mean(samples_hmc$mu_U2_SARS_Ang),
                                                           sigma_U2_SARS_Ang = mean(samples_hmc$sigma_U2_SARS_Ang),
                                                           beta0_U_SARS_AngToSARS_COV2 = mean(samples_hmc$beta0_U_SARS_AngToSARS_COV2),
                                                           beta_U1_SARS_AngToSARS_COV2 = mean(samples_hmc$beta_U1_SARS_AngToSARS_COV2),
                                                           beta_U2_SARS_AngToSARS_COV2 = mean(samples_hmc$beta_U2_SARS_AngToSARS_COV2),
                                                           beta0_SARS_COV2ToACE2 = mean(samples_hmc$beta0_SARS_COV2ToACE2),
                                                           beta_SARS_COV2ToACE2 = mean(samples_hmc$beta_SARS_COV2ToACE2),
                                                           beta0_ACE2_and_U_SARS_Ang_ToAng = mean(samples_hmc$beta0_ACE2_and_U_SARS_Ang_ToAng),
                                                           beta_ACE2ToAng = mean(samples_hmc$beta_ACE2ToAng),
                                                           beta_U1_SARS_AngToAng = mean(samples_hmc$beta_U1_SARS_AngToAng),
                                                           beta_U2_SARS_AngToAng = mean(samples_hmc$beta_U2_SARS_AngToAng),
                                                           beta0_AngToAGTR1 = mean(samples_hmc$beta0_AngToAGTR1),
                                                           beta_AngToAGTR1 = mean(samples_hmc$beta_AngToAGTR1),
                                                           mu_U1_ADAM17_Sil6r = mean(samples_hmc$mu_U1_ADAM17_Sil6r),
                                                           sigma_U1_ADAM17_Sil6r = mean(samples_hmc$sigma_U1_ADAM17_Sil6r),
                                                           mu_U2_ADAM17_Sil6r = mean(samples_hmc$mu_U2_ADAM17_Sil6r),
                                                           sigma_U2_ADAM17_Sil6r = mean(samples_hmc$sigma_U2_ADAM17_Sil6r),
                                                           beta0_AGTR1_UToADAM17 = mean(samples_hmc$beta0_AGTR1_UToADAM17),
                                                           beta_AGTR1ToADAM17 = mean(samples_hmc$beta_AGTR1ToADAM17),
                                                           beta_U1_ADAM17_Sil6rToADAM17 = mean(samples_hmc$beta_U1_ADAM17_Sil6rToADAM17),
                                                           beta_U2_ADAM17_Sil6rToADAM17 = mean(samples_hmc$beta_U2_ADAM17_Sil6rToADAM17),
                                                           mu_Toci = mean(samples_hmc$mu_Toci),
                                                           sigma_Toci = mean(samples_hmc$sigma_Toci),
                                                           beta0_ADAM17_U_TociToSil6r = mean(samples_hmc$beta0_ADAM17_U_TociToSil6r),
                                                           beta_ADAM17ToSil6r = mean(samples_hmc$beta_ADAM17ToSil6r),
                                                           beta_U1ToSil6r = mean(samples_hmc$beta_U1ToSil6r),
                                                           beta_U2ToSil6r = mean(samples_hmc$beta_U2ToSil6r),
                                                           beta_TociToSil6r = mean(samples_hmc$beta_TociToSil6r),
                                                           mu_U_EGF_EGFR = mean(samples_hmc$mu_U_EGF_EGFR),
                                                           sigma_U_EGF_EGFR = mean(samples_hmc$sigma_U_EGF_EGFR),
                                                           beta0_ADAM17_UToEGF = mean(samples_hmc$beta0_ADAM17_UToEGF),
                                                           beta_ADAM17ToEGF = mean(samples_hmc$beta_ADAM17ToEGF),
                                                           beta_UToEGF = mean(samples_hmc$beta_UToEGF),
                                                           mu_U_EGFR_TNF = mean(samples_hmc$mu_U_EGFR_TNF),
                                                           sigma_U_EGFR_TNF = mean(samples_hmc$sigma_U_EGFR_TNF),
                                                           beta0_ADAM17_UToTNF = mean(samples_hmc$beta0_ADAM17_UToTNF),
                                                           beta_ADAM17ToTNF = mean(samples_hmc$beta_ADAM17ToTNF),
                                                           beta_UToTNF = mean(samples_hmc$beta_UToTNF),
                                                           mu_U_EGFR_IL6STAT3 = mean(samples_hmc$mu_U_EGFR_IL6STAT3),
                                                           sigma_U_EGFR_IL6STAT3 = mean(samples_hmc$sigma_U_EGFR_IL6STAT3),
                                                           beta0_EGF_3U = mean(samples_hmc$beta0_EGF_3U),
                                                           beta_EGFToEGFR = mean(samples_hmc$beta_EGFToEGFR),
                                                           beta_U1ToEGFR = mean(samples_hmc$beta_U1ToEGFR),
                                                           beta_U2ToEGFR = mean(samples_hmc$beta_U2ToEGFR),
                                                           beta_U3ToEGFR = mean(samples_hmc$beta_U3ToEGFR),
                                                           beta_GefiToEGFR = mean(samples_hmc$beta_GefiToEGFR),
                                                           mu_U1_PRR_NFKB = mean(samples_hmc$mu_U1_PRR_NFKB),
                                                           sigma_U1_PRR_NFKB = mean(samples_hmc$sigma_U1_PRR_NFKB),
                                                           mu_U2_PRR_NFKB = mean(samples_hmc$mu_U2_PRR_NFKB),
                                                           sigma_U2_PRR_NFKB = mean(samples_hmc$sigma_U2_PRR_NFKB),
                                                           beta0_SARS_UPRR = mean(samples_hmc$beta0_SARS_UPRR),
                                                           beta_SARS_COV2ToPRR = mean(samples_hmc$beta_SARS_COV2ToPRR),
                                                           beta_U1ToPRR = mean(samples_hmc$beta_U1ToPRR),
                                                           beta_U2ToPRR = mean(samples_hmc$beta_U2ToPRR),
                                                           beta0_PRR_U_EGFR_TNFToNFKB = mean(samples_hmc$beta0_PRR_U_EGFR_TNFToNFKB),
                                                           beta_PRRToNFKB = mean(samples_hmc$beta_PRRToNFKB),
                                                           beta_U1ToNFKB = mean(samples_hmc$beta_U1ToNFKB),
                                                           beta_U2ToNFKB = mean(samples_hmc$beta_U2ToNFKB),
                                                           beta_EGFRToNFKB = mean(samples_hmc$beta_EGFRToNFKB),
                                                           beta_TNFToNFKB = mean(samples_hmc$beta_TNFToNFKB),
                                                           beta0_NFKB_IL6STSTToIL6STAT3 = mean(samples_hmc$beta0_NFKB_IL6STSTToIL6STAT3),
                                                           beta_UToIL6STAT3 = mean(samples_hmc$beta_UToIL6STAT3),
                                                           beta_Sil6rToIL6STAT3 = mean(samples_hmc$beta_Sil6rToIL6STAT3),
                                                           beta0_NFKB_IL6STATToIL6AMP = mean(samples_hmc$beta0_NFKB_IL6STATToIL6AMP),
                                                           beta_NFKBToIL6AMP = mean(samples_hmc$beta_NFKBToIL6AMP),
                                                           beta_IL6STAT3ToIL6AMP = mean(samples_hmc$beta_IL6STAT3ToIL6AMP),
                                                           beta0_IL6AMPTocytok= mean(samples_hmc$beta0_IL6AMPTocytok),
                                                           beta_IL6AMPTocytok = mean(samples_hmc$beta_IL6AMPTocytok),
                                                           mu_Gefi = mean(samples_hmc$mu_Gefi),
                                                           sigma_Gefi = mean(samples_hmc$sigma_Gefi),
                                                           seed = seed,
                                                           data_count = data_count
    )
    means_hmc <- c(means_hmc,abs(mean(estimated_y_hmc_list[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list_egfr[[data_count]]$cytok)))
  }
  means_hmc_list[[paste0("num_data_points_",num_data_points)]] <- means_hmc
  means_hmc <- c()
}
end_time <- Sys.time()
end_time - start_time
saveRDS(means_hmc_list,file = "data/Case3_Covid/output/means_hmc_list_Case3_egfr.RData")
```





# The misspecified model

## Misspecified Stan model in presence of latent variables

```{r}
model_str_covid_misspecify <- "
    data {
        int D;
        vector[D] SARS_COV2;
        vector[D] ACE2;
        vector[D] Ang;
        vector[D] AGTR1;
        vector[D] ADAM17;
        vector[D] Toci;
        vector[D] Sil6r;
        vector[D] EGF;
        vector[D] TNF;
        vector[D] Gefi;
        vector[D] EGFR;
        vector[D] PRR;
        vector[D] NFKB;
        vector[D] IL6STAT3;
        vector[D] IL6AMP;
        int<lower=0,upper=1> cytok[D];
    }
    parameters {
       real<lower=0> mu_U_SARS_Ang; 
       real<lower=0> sigma_U_SARS_Ang;
       real beta0_U_SARS_AngToSARS_COV2;
       real<lower=0> beta_U_SARS_AngToSARS_COV2;
       real<lower=10, upper=30> beta0_SARS_COV2ToACE2;
       real<upper=0> beta_SARS_COV2ToACE2;
       real<lower=10, upper=30> beta0_ACE2_and_U_SARS_Ang_ToAng;
       real<upper=0> beta_ACE2ToAng;
       real<lower=0> beta_U_SARS_AngToAng;
       real beta0_AngToAGTR1;
       real<lower=0> beta_AngToAGTR1;
       real<lower=0> mu_U_ADAM17_Sil6r;
       real<lower=0> sigma_U_ADAM17_Sil6r;
       real beta0_AGTR1_UToADAM17;
       real<lower=0> beta_AGTR1ToADAM17;
       real<lower=0> beta_U_ADAM17_Sil6rToADAM17;
       real<lower=0> mu_Toci;
       real<lower=0> sigma_Toci;
       real beta0_ADAM17_U_TociToSil6r;
       real<lower=0> beta_ADAM17ToSil6r;
       real<lower=0> beta_UToSil6r;
       real<upper=0> beta_TociToSil6r;
       real<lower=0> mu_U_EGF_EGFR;
       real<lower=0> sigma_U_EGF_EGFR;
       real beta0_ADAM17_UToEGF;
       real<lower=0> beta_ADAM17ToEGF;
       real<lower=0> beta_UToEGF;
       real<lower=0> mu_U_EGFR_TNF;
       real<lower=0> sigma_U_EGFR_TNF;
       real beta0_ADAM17_UToTNF;
       real<lower=0> beta_ADAM17ToTNF;
       real<lower=0> beta_UToTNF;
       real<lower=0> mu_U_EGFR_IL6STAT3;
       real<lower=0> sigma_U_EGFR_IL6STAT3;
       real beta0_EGF_3U;
       real<lower=0> mu_Gefi;
       real<lower=0> sigma_Gefi;
       real<lower=0> beta_EGFToEGFR;
       real<lower=0> beta_U1ToEGFR;
       real<lower=0> beta_U2ToEGFR;
       real<lower=0> beta_U3ToEGFR; 
       real<upper=0> beta_GefiToEGFR;
       real<lower=0> mu_U_PRR_NFKB;
       real<lower=0> sigma_U_PRR_NFKB;
       real beta0_SARS_UPRR;
       real<lower=0> beta_SARS_COV2ToPRR;
       real<lower=0> beta_UToPRR;
       real beta0_PRR_U_EGFR_TNFToNFKB;
       real<lower=0> beta_PRRToNFKB;
       real<lower=0> beta_UToNFKB;
       real<lower=0> beta_EGFRToNFKB;
       real<lower=0> beta_TNFToNFKB;
       real beta0_NFKB_IL6STSTToIL6STAT3;
       real<lower=0> beta_UToIL6STAT3;
       real<lower=0> beta_Sil6rToIL6STAT3;
       real beta0_NFKB_IL6STATToIL6AMP;
       real<lower=0> beta_NFKBToIL6AMP;
       real<lower=0> beta_IL6STAT3ToIL6AMP;
       real beta0_IL6AMPTocytok;
       real<lower=0> beta_IL6AMPTocytok;
       vector[D] U_SARS_Ang;
       vector[D] U_ADAM17_Sil6r;
       vector[D] U_EGF_EGFR;
       vector[D] U_EGFR_TNF;
       vector[D] U_EGFR_IL6STAT3;
       vector[D] U_PRR_NFKB;
    }
    transformed parameters {
      vector[D] SARS_COV2_loc;
      vector[D] ACE2_loc;
      vector[D] Ang_loc;
      vector[D] AGTR1_loc;
      vector[D] ADAM17_loc;
      vector[D] Sil6r_loc;
      vector[D] EGF_loc;
      vector[D] TNF_loc;
      vector[D] EGFR_loc;
      vector[D] PRR_loc;
      vector[D] NFKB_loc;
      vector[D] IL6STAT3_loc;
      vector[D] IL6AMP_loc;
      for (i in 1:D){
        SARS_COV2_loc[i] = 100 / (1 + exp(-beta0_U_SARS_AngToSARS_COV2 -U_SARS_Ang[i] * beta_U_SARS_AngToSARS_COV2));
        ACE2_loc[i] = beta0_SARS_COV2ToACE2 + SARS_COV2[i] * beta_SARS_COV2ToACE2;
        Ang_loc[i] = beta0_ACE2_and_U_SARS_Ang_ToAng + ACE2[i] * beta_ACE2ToAng + U_SARS_Ang[i] * beta_U_SARS_AngToAng;
        AGTR1_loc[i] = 100 / (1 + exp(-beta0_AngToAGTR1 - Ang[i] * beta_AngToAGTR1));
        ADAM17_loc[i] = 100 / (1 + exp(-beta0_AGTR1_UToADAM17 - AGTR1[i] * beta_AGTR1ToADAM17 - U_ADAM17_Sil6r[i] * beta_U_ADAM17_Sil6rToADAM17));
        Sil6r_loc[i] = 100 / (1 + exp(-beta0_ADAM17_U_TociToSil6r - ADAM17[i] * beta_ADAM17ToSil6r - U_ADAM17_Sil6r[i] * beta_UToSil6r - Toci[i] * beta_TociToSil6r));
        EGF_loc[i] = 100 / (1 + exp(-beta0_ADAM17_UToEGF - ADAM17[i] * beta_ADAM17ToEGF - U_EGF_EGFR[i] * beta_UToEGF));
        TNF_loc[i] = 100 / (1 + exp(-beta0_ADAM17_UToTNF - ADAM17[i] * beta_ADAM17ToTNF - U_EGFR_TNF[i] * beta_UToTNF));
        EGFR_loc[i] = 100 / (1 + exp(-beta0_EGF_3U - EGF[i] * beta_EGFToEGFR - U_EGFR_IL6STAT3[i] * beta_U1ToEGFR - U_EGFR_TNF[i] * beta_U2ToEGFR  - U_EGF_EGFR[i] * beta_U3ToEGFR - Gefi[i] * beta_GefiToEGFR));
        PRR_loc[i] = 100 / (1 + exp(-beta0_SARS_UPRR - SARS_COV2[i] * beta_SARS_COV2ToPRR - U_PRR_NFKB[i] * beta_UToPRR));
        NFKB_loc[i] = 100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR[i] * beta_PRRToNFKB - U_PRR_NFKB[i] * beta_UToNFKB - EGFR[i] * beta_EGFRToNFKB  - TNF[i] * beta_TNFToNFKB));
        IL6STAT3_loc[i] = 100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3[i] * beta_UToIL6STAT3 - Sil6r[i] * beta_Sil6rToIL6STAT3));
        IL6AMP_loc[i] = 100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB[i] * beta_NFKBToIL6AMP - IL6STAT3[i] * beta_IL6STAT3ToIL6AMP));
      }
    }
    model {
        mu_U_SARS_Ang ~ normal(45, 1); 
        sigma_U_SARS_Ang ~ normal(10, 1); 
        beta0_U_SARS_AngToSARS_COV2 ~ normal(0, 10);
        beta_U_SARS_AngToSARS_COV2 ~ normal(0,10);
        beta0_SARS_COV2ToACE2 ~ normal(20,10);
        beta_SARS_COV2ToACE2 ~ normal(0,10);
        beta0_ACE2_and_U_SARS_Ang_ToAng ~ normal(20,10);
        beta_ACE2ToAng ~ normal(0,10);
        beta_U_SARS_AngToAng ~ normal(0,10);
        beta0_AngToAGTR1 ~ normal(0,10);
        beta_AngToAGTR1 ~ normal(0,10);
        beta0_AGTR1_UToADAM17 ~ normal(0,10);
        beta_AGTR1ToADAM17 ~ normal(0,10);
        beta_U_ADAM17_Sil6rToADAM17 ~ normal(0,10);
        mu_Toci ~ normal(45, 1);
        sigma_Toci ~ normal(10, 1);
        beta0_ADAM17_U_TociToSil6r ~ normal(0, 10);
        beta_ADAM17ToSil6r ~ normal(0, 10);
        beta_UToSil6r ~ normal(0, 10);
        beta_TociToSil6r ~ normal(0, 10);
        mu_U_EGF_EGFR ~ normal(50,1);
        sigma_U_EGF_EGFR ~ normal(10,1);
        beta0_ADAM17_UToEGF ~ normal(0,10);
        beta_ADAM17ToEGF ~ normal(0,10);
        beta_UToEGF ~ normal(0,10);
        mu_U_EGFR_TNF ~ normal(45,1);
        sigma_U_EGFR_TNF ~ normal(10,1);
        beta0_ADAM17_UToTNF ~ normal(0, 10);
        beta_ADAM17ToTNF ~ normal(0, 10);
        beta_UToTNF ~ normal(0, 10);
        mu_U_EGFR_IL6STAT3 ~ normal(40,1);
        sigma_U_EGFR_IL6STAT3 ~ normal(10,1);
        beta0_EGF_3U ~ normal(0, 10);
        mu_Gefi ~ normal(40,1);
        sigma_Gefi ~ normal(10,1);
        beta_EGFToEGFR ~ normal(0, 10);
        beta_U1ToEGFR ~ normal(0, 10);
        beta_U2ToEGFR ~ normal(0, 10);
        beta_U3ToEGFR ~ normal(0, 10); 
        beta_GefiToEGFR ~ normal(0, 10);
        mu_U_PRR_NFKB ~ normal(40, 1);
        sigma_U_PRR_NFKB ~ normal(10,1);
        beta0_SARS_UPRR ~ normal(0, 10);
        beta_SARS_COV2ToPRR ~ normal(0, 10);
        beta_UToPRR ~ normal(0, 10);
        beta_PRRToNFKB ~ normal(0, 10);
        beta_UToNFKB ~ normal(0, 10);
        beta_EGFRToNFKB ~ normal(0, 10);
        beta_TNFToNFKB ~ normal(0, 10);
        beta0_NFKB_IL6STSTToIL6STAT3 ~ normal(0, 10);
        beta_UToIL6STAT3 ~ normal(0, 10);
        beta_Sil6rToIL6STAT3 ~ normal(0, 10);
        beta0_NFKB_IL6STATToIL6AMP ~ normal(0, 10);
        beta_NFKBToIL6AMP ~ normal(0, 10);
        beta_IL6STAT3ToIL6AMP ~ normal(0, 10); 
        beta0_IL6AMPTocytok ~ normal(0, 10);
        beta_IL6AMPTocytok ~ normal(0, 10);         
        //
        U_SARS_Ang ~ normal(mu_U_SARS_Ang, sigma_U_SARS_Ang);      // likelihood
        SARS_COV2 ~ normal(SARS_COV2_loc, 101);
        ACE2 ~ normal(ACE2_loc,1.6);
        Ang ~ normal(Ang_loc,6);
        AGTR1 ~ normal(AGTR1_loc,7.6);
        ADAM17 ~ normal(ADAM17_loc,8.7);
        U_ADAM17_Sil6r ~ normal(mu_U_ADAM17_Sil6r, sigma_U_ADAM17_Sil6r);
        Toci ~ normal(mu_Toci, sigma_Toci);
        Sil6r ~ normal(Sil6r_loc,17.9);
        U_EGF_EGFR ~ normal(mu_U_EGF_EGFR, sigma_U_EGF_EGFR);
        EGF ~ normal(EGF_loc,7);
        U_EGFR_TNF ~ normal(mu_U_EGFR_TNF,sigma_U_EGFR_TNF);
        TNF ~ normal(TNF_loc, 6.5);
        U_EGFR_IL6STAT3 ~ normal(mu_U_EGFR_IL6STAT3, sigma_U_EGFR_IL6STAT3);
        Gefi ~ normal(mu_Gefi, sigma_Gefi);
        EGFR ~ normal(EGFR_loc, 13.3);
        U_PRR_NFKB ~ normal(mu_U_PRR_NFKB,sigma_U_PRR_NFKB);
        PRR ~ normal(PRR_loc,14.1);
        NFKB ~ normal(NFKB_loc,10);
        IL6STAT3 ~ normal(IL6STAT3_loc, 18.6);
        IL6AMP ~ normal(IL6AMP_loc, 12);
        for(i in 1:D) {
        cytok[i] ~ bernoulli_logit(beta0_IL6AMPTocytok + IL6AMP[i] * beta_IL6AMPTocytok);
        }
    }
"
```

```{r, message=FALSE, warning=FALSE}
mod_misspecify <- rstan::stan_model(model_code = model_str_covid_misspecify)
```

## Mutilated model

```{r}
parameters_misspecify <- c("mu_U_SARS_Ang", "sigma_U_SARS_Ang"
                                     ,"beta0_U_SARS_AngToSARS_COV2","beta_U_SARS_AngToSARS_COV2"
                                     ,"beta0_SARS_COV2ToACE2", "beta_SARS_COV2ToACE2"
                                     ,"beta0_ACE2_and_U_SARS_Ang_ToAng", "beta_ACE2ToAng", "beta_U_SARS_AngToAng"
                                     ,"beta0_AngToAGTR1", "beta_AngToAGTR1"
                                     ,"mu_U_ADAM17_Sil6r", "sigma_U_ADAM17_Sil6r"
                                     ,"beta0_AGTR1_UToADAM17", "beta_AGTR1ToADAM17","beta_U_ADAM17_Sil6rToADAM17"
                                     ,"mu_Toci", "sigma_Toci"
                                     ,"beta0_ADAM17_U_TociToSil6r", "beta_ADAM17ToSil6r", "beta_UToSil6r", "beta_TociToSil6r"
                                     ,"mu_U_EGF_EGFR", "sigma_U_EGF_EGFR"
                                     ,"beta0_ADAM17_UToEGF", "beta_ADAM17ToEGF", "beta_UToEGF"
                                     ,"mu_U_EGFR_TNF", "sigma_U_EGFR_TNF"
                                     ,"beta0_ADAM17_UToTNF", "beta_ADAM17ToTNF", "beta_UToTNF"
                                     ,"mu_U_EGFR_IL6STAT3", "sigma_U_EGFR_IL6STAT3"
                                     ,"beta0_EGF_3U", "beta_EGFToEGFR", "beta_U1ToEGFR", "beta_U2ToEGFR", "beta_U3ToEGFR", "beta_GefiToEGFR"
                                     ,"mu_U_PRR_NFKB", "sigma_U_PRR_NFKB"
                                     ,"beta0_SARS_UPRR", "beta_SARS_COV2ToPRR", "beta_UToPRR"
                                     ,"beta0_PRR_U_EGFR_TNFToNFKB", "beta_PRRToNFKB", "beta_UToNFKB", "beta_EGFRToNFKB", "beta_TNFToNFKB"  
                                     ,"beta0_NFKB_IL6STSTToIL6STAT3", "beta_UToIL6STAT3", "beta_Sil6rToIL6STAT3"
                                     ,"beta0_NFKB_IL6STATToIL6AMP", "beta_NFKBToIL6AMP", "beta_IL6STAT3ToIL6AMP"
                                     ,"beta0_IL6AMPTocytok", "beta_IL6AMPTocytok", "mu_Gefi", "sigma_Gefi")
```

```{r}
num_samples = 1000
mutilated_model_misspecify_sil6r <- function(mu_U_SARS_Ang, sigma_U_SARS_Ang
                            ,beta0_U_SARS_AngToSARS_COV2,beta_U_SARS_AngToSARS_COV2
                            ,beta0_SARS_COV2ToACE2, beta_SARS_COV2ToACE2
                            ,beta0_ACE2_and_U_SARS_Ang_ToAng, beta_ACE2ToAng, beta_U_SARS_AngToAng
                            ,beta0_AngToAGTR1, beta_AngToAGTR1
                            ,mu_U_ADAM17_Sil6r,sigma_U_ADAM17_Sil6r
                            ,beta0_AGTR1_UToADAM17,beta_AGTR1ToADAM17, beta_U_ADAM17_Sil6rToADAM17
                            ,mu_Toci, sigma_Toci
                            ,beta0_ADAM17_U_TociToSil6r, beta_ADAM17ToSil6r, beta_UToSil6r, beta_TociToSil6r
                            ,mu_U_EGF_EGFR, sigma_U_EGF_EGFR
                            ,beta0_ADAM17_UToEGF, beta_ADAM17ToEGF, beta_UToEGF
                            ,mu_U_EGFR_TNF, sigma_U_EGFR_TNF
                            ,beta0_ADAM17_UToTNF, beta_ADAM17ToTNF, beta_UToTNF
                            ,mu_U_EGFR_IL6STAT3,sigma_U_EGFR_IL6STAT3
                            ,beta0_EGF_3U, beta_EGFToEGFR, beta_U1ToEGFR, beta_U2ToEGFR, beta_U3ToEGFR, beta_GefiToEGFR
                            ,mu_U_PRR_NFKB, sigma_U_PRR_NFKB
                            ,beta0_SARS_UPRR, beta_SARS_COV2ToPRR, beta_UToPRR
                            ,beta0_PRR_U_EGFR_TNFToNFKB, beta_PRRToNFKB, beta_UToNFKB, beta_EGFRToNFKB, beta_TNFToNFKB
                            ,beta0_NFKB_IL6STSTToIL6STAT3, beta_UToIL6STAT3, beta_Sil6rToIL6STAT3
                            ,beta0_NFKB_IL6STATToIL6AMP, beta_NFKBToIL6AMP, beta_IL6STAT3ToIL6AMP
                            ,beta0_IL6AMPTocytok, beta_IL6AMPTocytok
                            ,mu_Gefi, sigma_Gefi
                            ,seed, data_count
) {
    set.seed(seed)
    U_SARS_Ang_1 <- rnorm(num_samples, mu_U_SARS_Ang, sigma_U_SARS_Ang)
    SARS_COV2_1 = #rnorm(num_samples,
                        100 / (1 + exp(-beta0_U_SARS_AngToSARS_COV2 - U_SARS_Ang_1 * beta_U_SARS_AngToSARS_COV2))#,
                        #sqrt(var(obs_data_list[[data_count]]$SARS_COV2))
                        #)
    ACE2_1 = #rnorm(num_samples,
                   beta0_SARS_COV2ToACE2 + SARS_COV2_1 * beta_SARS_COV2ToACE2#,
                   #sqrt(var(obs_data_list[[data_count]]$ACE2))
                   #)
    Ang_1 = #rnorm(num_samples,
                  beta0_ACE2_and_U_SARS_Ang_ToAng + ACE2_1 * beta_ACE2ToAng + U_SARS_Ang_1 *beta_U_SARS_AngToAng#,
                  #sqrt(var(obs_data_list[[data_count]]$Ang))
                  #)
    AGTR1_1 = #rnorm(num_samples,
                    100 / (1 + exp(-beta0_AngToAGTR1 - Ang_1 * beta_AngToAGTR1))#,
                    #sqrt(var(obs_data_list[[data_count]]$AGTR1))
                    #)
    U_ADAM17_Sil6r_1 = rnorm(num_samples,mu_U_ADAM17_Sil6r,sigma_U_ADAM17_Sil6r)
    ADAM17_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_AGTR1_UToADAM17 - AGTR1_1 * beta_AGTR1ToADAM17 - U_ADAM17_Sil6r_1 * beta_U_ADAM17_Sil6rToADAM17))#,
                     #sqrt(var(obs_data_list[[data_count]]$ADAM17))
                     #)
    Toci_1 = rnorm(num_samples,mu_Toci, sigma_Toci)
    
    Sil6r_1 = rep(20, num_samples)
    
    U_EGF_EGFR_1 = rnorm(num_samples, mu_U_EGF_EGFR, sigma_U_EGF_EGFR)
    EGF_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_UToEGF - ADAM17_1 * beta_ADAM17ToEGF - U_EGF_EGFR_1 * beta_UToEGF))#,
                  #sqrt(var(obs_data_list[[data_count]]$EGF))
                  #)
    U_EGFR_TNF_1 = rnorm(num_samples, mu_U_EGFR_TNF, sigma_U_EGFR_TNF)
    TNF_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_UToTNF - ADAM17_1 * beta_ADAM17ToTNF - U_EGFR_TNF_1 * beta_UToTNF))# ,
                  #sqrt(var(obs_data_list[[data_count]]$TNF))
                  #)
    U_EGFR_IL6STAT3_1 =  rnorm(num_samples, mu_U_EGFR_IL6STAT3, sigma_U_EGFR_IL6STAT3)
    Gefi_1 = rnorm(num_samples,mu_Gefi, sigma_Gefi)
    EGFR_1 = #rnorm(num_samples,
                   100 / (1 + exp(-beta0_EGF_3U - EGF_1 * beta_EGFToEGFR - U_EGFR_IL6STAT3_1 * beta_U1ToEGFR - U_EGFR_TNF_1 * beta_U2ToEGFR  - U_EGF_EGFR_1 * beta_U3ToEGFR - Gefi_1 * beta_GefiToEGFR))#,
                   #sqrt(var(obs_data_list[[data_count]]$EGFR))
                   #)
    U_PRR_NFKB_1 = rnorm(num_samples, mu_U_PRR_NFKB, sigma_U_PRR_NFKB)
    PRR_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_SARS_UPRR - SARS_COV2_1 * beta_SARS_COV2ToPRR - U_PRR_NFKB_1 * beta_UToPRR))# ,
                  #sqrt(var(obs_data_list[[data_count]]$PRR))
                  #)
    NFKB_1 = #rnorm(num_samples,
                   100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR_1 * beta_PRRToNFKB - U_PRR_NFKB_1 * beta_UToNFKB - EGFR_1 * beta_EGFRToNFKB  - TNF_1 * beta_TNFToNFKB))# ,
                   #sqrt(var(obs_data_list[[data_count]]$NFKB))
                   #)
    IL6STAT3_1 = #rnorm(num_samples,
                       100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3_1 * beta_UToIL6STAT3 - Sil6r_1 * beta_Sil6rToIL6STAT3))#,
                       #sqrt(var(obs_data_list[[data_count]]$IL6STAT3))
                       #)
    IL6AMP_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB_1 * beta_NFKBToIL6AMP - IL6STAT3_1 * beta_IL6STAT3ToIL6AMP))#,
                     #sqrt(var(obs_data_list[[data_count]]$IL6AMP))
                     #)
    p_cytok = 1 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP_1 * beta_IL6AMPTocytok))
    cytok_1 = rbinom(n = num_samples, size = 1, prob = p_cytok)
    return(cytok_1)
}
```


```{r}
num_samples = 1000
mutilated_model_misspecify_egfr <- function(mu_U_SARS_Ang, sigma_U_SARS_Ang
                            ,beta0_U_SARS_AngToSARS_COV2,beta_U_SARS_AngToSARS_COV2
                            ,beta0_SARS_COV2ToACE2, beta_SARS_COV2ToACE2
                            ,beta0_ACE2_and_U_SARS_Ang_ToAng, beta_ACE2ToAng, beta_U_SARS_AngToAng
                            ,beta0_AngToAGTR1, beta_AngToAGTR1
                            ,mu_U_ADAM17_Sil6r,sigma_U_ADAM17_Sil6r
                            ,beta0_AGTR1_UToADAM17,beta_AGTR1ToADAM17, beta_U_ADAM17_Sil6rToADAM17
                            ,mu_Toci, sigma_Toci
                            ,beta0_ADAM17_U_TociToSil6r, beta_ADAM17ToSil6r, beta_UToSil6r, beta_TociToSil6r
                            ,mu_U_EGF_EGFR, sigma_U_EGF_EGFR
                            ,beta0_ADAM17_UToEGF, beta_ADAM17ToEGF, beta_UToEGF
                            ,mu_U_EGFR_TNF, sigma_U_EGFR_TNF
                            ,beta0_ADAM17_UToTNF, beta_ADAM17ToTNF, beta_UToTNF
                            ,mu_U_EGFR_IL6STAT3,sigma_U_EGFR_IL6STAT3
                            ,beta0_EGF_3U, beta_EGFToEGFR, beta_U1ToEGFR, beta_U2ToEGFR, beta_U3ToEGFR, beta_GefiToEGFR
                            ,mu_U_PRR_NFKB, sigma_U_PRR_NFKB
                            ,beta0_SARS_UPRR, beta_SARS_COV2ToPRR, beta_UToPRR
                            ,beta0_PRR_U_EGFR_TNFToNFKB, beta_PRRToNFKB, beta_UToNFKB, beta_EGFRToNFKB, beta_TNFToNFKB
                            ,beta0_NFKB_IL6STSTToIL6STAT3, beta_UToIL6STAT3, beta_Sil6rToIL6STAT3
                            ,beta0_NFKB_IL6STATToIL6AMP, beta_NFKBToIL6AMP, beta_IL6STAT3ToIL6AMP
                            ,beta0_IL6AMPTocytok, beta_IL6AMPTocytok
                            ,mu_Gefi, sigma_Gefi
                            ,seed, data_count
) {
    set.seed(seed)
    U_SARS_Ang_1 <- rnorm(num_samples, mu_U_SARS_Ang, sigma_U_SARS_Ang)
    SARS_COV2_1 = #rnorm(num_samples,
                        100 / (1 + exp(-beta0_U_SARS_AngToSARS_COV2 - U_SARS_Ang_1 * beta_U_SARS_AngToSARS_COV2))#,
                        #sqrt(var(obs_data_list[[data_count]]$SARS_COV2))
                        #)
    ACE2_1 = #rnorm(num_samples,
                   beta0_SARS_COV2ToACE2 + SARS_COV2_1 * beta_SARS_COV2ToACE2#,
                   #sqrt(var(obs_data_list[[data_count]]$ACE2))
                   #)
    Ang_1 = #rnorm(num_samples,
                  beta0_ACE2_and_U_SARS_Ang_ToAng + ACE2_1 * beta_ACE2ToAng + U_SARS_Ang_1 *beta_U_SARS_AngToAng#,
                  #sqrt(var(obs_data_list[[data_count]]$Ang))
                  #)
    AGTR1_1 = #rnorm(num_samples,
                    100 / (1 + exp(-beta0_AngToAGTR1 - Ang_1 * beta_AngToAGTR1))#,
                    #sqrt(var(obs_data_list[[data_count]]$AGTR1))
                    #)
    U_ADAM17_Sil6r_1 = rnorm(num_samples,mu_U_ADAM17_Sil6r,sigma_U_ADAM17_Sil6r)
    ADAM17_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_AGTR1_UToADAM17 - AGTR1_1 * beta_AGTR1ToADAM17 - U_ADAM17_Sil6r_1 * beta_U_ADAM17_Sil6rToADAM17))#,
                     #sqrt(var(obs_data_list[[data_count]]$ADAM17))
                     #)
    Toci_1 = rnorm(num_samples,mu_Toci, sigma_Toci)
    
    #Sil6r_1 = rep(20, num_samples)
    Sil6r_1 = #rnorm(num_samples,
      100 / (1 + exp(-beta0_ADAM17_U_TociToSil6r - ADAM17_1 * beta_ADAM17ToSil6r - U_ADAM17_Sil6r_1 * beta_UToSil6r - Toci_1 * beta_TociToSil6r))#,
    #sqrt(var(obs_data_list[[data_count]]$EGF))
    #)
    
    U_EGF_EGFR_1 = rnorm(num_samples, mu_U_EGF_EGFR, sigma_U_EGF_EGFR)
    EGF_1 = #rnorm(num_samples,
                  100 / (1 + exp(-beta0_ADAM17_UToEGF - ADAM17_1 * beta_ADAM17ToEGF - U_EGF_EGFR_1 * beta_UToEGF))#,
                  #sqrt(var(obs_data_list[[data_count]]$EGF))
                  #)
    U_EGFR_TNF_1 = rnorm(num_samples, mu_U_EGFR_TNF, sigma_U_EGFR_TNF)
    TNF_1 = #rnorm(num_samples,
      100 / (1 + exp(-beta0_ADAM17_UToTNF - ADAM17_1 * beta_ADAM17ToTNF - U_EGFR_TNF_1 * beta_UToTNF))# ,
    #sqrt(var(obs_data_list[[data_count]]$TNF))
    #)
    U_EGFR_IL6STAT3_1 =  rnorm(num_samples, mu_U_EGFR_IL6STAT3, sigma_U_EGFR_IL6STAT3)
    Gefi_1 = rnorm(num_samples, mu_Gefi, sigma_Gefi)
    EGFR_1 = rep(20, num_samples)
    U_PRR_NFKB_1 = rnorm(num_samples, mu_U_PRR_NFKB, sigma_U_PRR_NFKB)
    PRR_1 = #rnorm(num_samples,
      100 / (1 + exp(-beta0_SARS_UPRR - SARS_COV2_1 * beta_SARS_COV2ToPRR - U_PRR_NFKB_1 * beta_UToPRR))# ,
    #sqrt(var(obs_data_list[[data_count]]$PRR))
    #)
    NFKB_1 = #rnorm(num_samples,
                   100 / (1 + exp(-beta0_PRR_U_EGFR_TNFToNFKB - PRR_1 * beta_PRRToNFKB - U_PRR_NFKB_1 * beta_UToNFKB - EGFR_1 * beta_EGFRToNFKB  - TNF_1 * beta_TNFToNFKB))# ,
                   #sqrt(var(obs_data_list[[data_count]]$NFKB))
                   #)
    IL6STAT3_1 = #rnorm(num_samples,
                       100 / (1 + exp(-beta0_NFKB_IL6STSTToIL6STAT3 - U_EGFR_IL6STAT3_1 * beta_UToIL6STAT3 - Sil6r_1 * beta_Sil6rToIL6STAT3))#,
                       #sqrt(var(obs_data_list[[data_count]]$IL6STAT3))
                       #)
    IL6AMP_1 = #rnorm(num_samples,
                     100 / (1 + exp(-beta0_NFKB_IL6STATToIL6AMP - NFKB_1 * beta_NFKBToIL6AMP - IL6STAT3_1 * beta_IL6STAT3ToIL6AMP))#,
                     #sqrt(var(obs_data_list[[data_count]]$IL6AMP))
                     #)
    p_cytok = 1 / (1 + exp(-beta0_IL6AMPTocytok - IL6AMP_1 * beta_IL6AMPTocytok))
    cytok_1 = rbinom(n = num_samples, size = 1, prob = p_cytok)
    return(cytok_1)
}
```


```{r}
# seed = 5
# hmc_fit_list_misspecify <- rep(list(list()), K)
# 
# start_time <- Sys.time()
# 
# for (num_data_points in ndp) {
#   print("num_data_points is:")
#   print(num_data_points)
#   for (data_count in 1:K) {
#     print("data_count is:")
#     print(data_count)
#     data_list <- list(D=num_data_points
#                       ,SARS_COV2 = obs_data_list[[data_count]]$SARS_COV2[1:num_data_points]
#                       ,ACE2 = obs_data_list[[data_count]]$ACE2[1:num_data_points]
#                       ,Ang = obs_data_list[[data_count]]$Ang[1:num_data_points]
#                       ,AGTR1 = obs_data_list[[data_count]]$AGTR1[1:num_data_points]
#                       ,ADAM17 = obs_data_list[[data_count]]$ADAM17[1:num_data_points]
#                       ,Toci = obs_data_list[[data_count]]$Toci[1:num_data_points]
#                       ,Sil6r = obs_data_list[[data_count]]$Sil6r[1:num_data_points]
#                       ,EGF = obs_data_list[[data_count]]$EGF[1:num_data_points]
#                       ,TNF = obs_data_list[[data_count]]$TNF[1:num_data_points]
#                       ,Gefi = obs_data_list[[data_count]]$Gefi[1:num_data_points]
#                       ,EGFR = obs_data_list[[data_count]]$EGFR[1:num_data_points]
#                       ,PRR = obs_data_list[[data_count]]$PRR[1:num_data_points]
#                       ,NFKB = obs_data_list[[data_count]]$NFKB[1:num_data_points]
#                       ,IL6STAT3= obs_data_list[[data_count]]$IL6STAT3[1:num_data_points]
#                       ,IL6AMP = obs_data_list[[data_count]]$IL6AMP[1:num_data_points]
#                       ,cytok = obs_data_list[[data_count]]$cytok[1:num_data_points]
#     )
# 
#     hmc_fit_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]] <- rstan::sampling(mod_misspecify, data=data_list, chains = 2, iter = 3000, warmup = 1500, seed = 2, control = list(max_treedepth = 15)) #seed = 1
#   }
# }
# 
# end_time <- Sys.time()
# end_time - start_time
# # Time difference of 2.749777 days
# saveRDS(hmc_fit_list_misspecify, file = "hmc_fit_list_misspecify.RData")
```

```{r}
hmc_fit_list_misspecify <- readRDS(file = "data/Case3_Covid/output/hmc_fit_list_Case3_misspecify.RData")

estimated_y_hmc_list_misspecify_egfr <- rep(list(list()), K)
estimated_y_hmc_list_misspecify_sil6r <- rep(list(list()), K)
means_hmc_misspecify_egfr <- c()
means_hmc_misspecify_sil6r <- c()
means_hmc_list_misspecify_egfr <- list()
means_hmc_list_misspecify_sil6r <- list()

for (num_data_points in ndp) {
  print("num_data_points is:")
  print(num_data_points)
  for (data_count in 1:K) {
    print("data_count is:")
    print(data_count)    
    samples_hmc_misspecify <- rstan::extract(hmc_fit_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]], parameters_misspecify)
    
    estimated_y_hmc_list_misspecify_egfr[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model_misspecify_egfr(
                                                                                 mu_U_SARS_Ang = mean(samples_hmc_misspecify$mu_U_SARS_Ang),
                                                                                 sigma_U_SARS_Ang = mean(samples_hmc_misspecify$sigma_U_SARS_Ang),
                                                                                 beta0_U_SARS_AngToSARS_COV2 = mean(samples_hmc_misspecify$beta0_U_SARS_AngToSARS_COV2),
                                                                                 beta_U_SARS_AngToSARS_COV2 = mean(samples_hmc_misspecify$beta_U_SARS_AngToSARS_COV2),
                                                                                 beta0_SARS_COV2ToACE2 = mean(samples_hmc_misspecify$beta0_SARS_COV2ToACE2),
                                                                                 beta_SARS_COV2ToACE2 = mean(samples_hmc_misspecify$beta_SARS_COV2ToACE2),
                                                                                 beta0_ACE2_and_U_SARS_Ang_ToAng = mean(samples_hmc_misspecify$beta0_ACE2_and_U_SARS_Ang_ToAng),
                                                                                 beta_ACE2ToAng = mean(samples_hmc_misspecify$beta_ACE2ToAng),
                                                                                 beta_U_SARS_AngToAng = mean(samples_hmc_misspecify$beta_U_SARS_AngToAng),
                                                                                 beta0_AngToAGTR1 = mean(samples_hmc_misspecify$beta0_AngToAGTR1),
                                                                                 beta_AngToAGTR1 = mean(samples_hmc_misspecify$beta_AngToAGTR1),
                                                                                 mu_U_ADAM17_Sil6r = mean(samples_hmc_misspecify$mu_U_ADAM17_Sil6r),
                                                                                 sigma_U_ADAM17_Sil6r = mean(samples_hmc_misspecify$sigma_U_ADAM17_Sil6r),
                                                                                 beta0_AGTR1_UToADAM17 = mean(samples_hmc_misspecify$beta0_AGTR1_UToADAM17),
                                                                                 beta_AGTR1ToADAM17 = mean(samples_hmc_misspecify$beta_AGTR1ToADAM17),
                                                                                 mean(samples_hmc_misspecify$beta_U_ADAM17_Sil6rToADAM17),
                                                                                 mean(samples_hmc_misspecify$mu_Toci),
                                                                                 mean(samples_hmc_misspecify$sigma_Toci),
                                                                                 mean(samples_hmc_misspecify$beta0_ADAM17_U_TociToSil6r),
                                                                                 mean(samples_hmc_misspecify$beta_ADAM17ToSil6r),
                                                                                 mean(samples_hmc_misspecify$beta_UToSil6r),
                                                                                 mean(samples_hmc_misspecify$beta_TociToSil6r),
                                                                                 mean(samples_hmc_misspecify$mu_U_EGF_EGFR),
                                                                                 mean(samples_hmc_misspecify$sigma_U_EGF_EGFR),
                                                                                 mean(samples_hmc_misspecify$beta0_ADAM17_UToEGF),
                                                                                 mean(samples_hmc_misspecify$beta_ADAM17ToEGF),
                                                                                 mean(samples_hmc_misspecify$beta_UToEGF),
                                                                                 mean(samples_hmc_misspecify$mu_U_EGFR_TNF),
                                                                                 mean(samples_hmc_misspecify$sigma_U_EGFR_TNF),
                                                                                 mean(samples_hmc_misspecify$beta0_ADAM17_UToTNF),
                                                                                 mean(samples_hmc_misspecify$beta_ADAM17ToTNF),
                                                                                 mean(samples_hmc_misspecify$beta_UToTNF),
                                                                                 mean(samples_hmc_misspecify$mu_U_EGFR_IL6STAT3),
                                                                                 mean(samples_hmc_misspecify$sigma_U_EGFR_IL6STAT3),
                                                                                 mean(samples_hmc_misspecify$beta0_EGF_3U),
                                                                                 mean(samples_hmc_misspecify$beta_EGFToEGFR),
                                                                                 mean(samples_hmc_misspecify$beta_U1ToEGFR),
                                                                                 mean(samples_hmc_misspecify$beta_U2ToEGFR),
                                                                                 mean(samples_hmc_misspecify$beta_U3ToEGFR),
                                                                                 beta_GefiToEGFR = mean(samples_hmc_misspecify$beta_GefiToEGFR),
                                                                                 mean(samples_hmc_misspecify$mu_U_PRR_NFKB),
                                                                                 mean(samples_hmc_misspecify$sigma_U_PRR_NFKB),
                                                                                 mean(samples_hmc_misspecify$beta0_SARS_UPRR),
                                                                                 mean(samples_hmc_misspecify$beta_SARS_COV2ToPRR),
                                                                                 mean(samples_hmc_misspecify$beta_UToPRR),
                                                                                 mean(samples_hmc_misspecify$beta0_PRR_U_EGFR_TNFToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_PRRToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_UToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_EGFRToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_TNFToNFKB),
                                                                                 beta0_NFKB_IL6STSTToIL6STAT3 = mean(samples_hmc_misspecify$beta0_NFKB_IL6STSTToIL6STAT3),
                                                                                 beta_UToIL6STAT3 = mean(samples_hmc_misspecify$beta_UToIL6STAT3),
                                                                                 beta_Sil6rToIL6STAT3 = mean(samples_hmc_misspecify$beta_Sil6rToIL6STAT3),
                                                                                 beta0_NFKB_IL6STATToIL6AMP = mean(samples_hmc_misspecify$beta0_NFKB_IL6STATToIL6AMP),
                                                                                 beta_NFKBToIL6AMP = mean(samples_hmc_misspecify$beta_NFKBToIL6AMP),
                                                                                 beta_IL6STAT3ToIL6AMP = mean(samples_hmc_misspecify$beta_IL6STAT3ToIL6AMP),
                                                                                 beta0_IL6AMPTocytok = mean(samples_hmc_misspecify$beta0_IL6AMPTocytok),
                                                                                 beta_IL6AMPTocytok = mean(samples_hmc_misspecify$beta_IL6AMPTocytok),
                                                                                 mu_Gefi = mean(samples_hmc_misspecify$mu_Gefi),
                                                                                 sigma_Gefi = mean(samples_hmc_misspecify$sigma_Gefi),
                                                                                 seed = seed, data_count = data_count
    )
    estimated_y_hmc_list_misspecify_sil6r[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model_misspecify_sil6r(
                                                                                 mu_U_SARS_Ang = mean(samples_hmc_misspecify$mu_U_SARS_Ang),
                                                                                 sigma_U_SARS_Ang = mean(samples_hmc_misspecify$sigma_U_SARS_Ang),
                                                                                 beta0_U_SARS_AngToSARS_COV2 = mean(samples_hmc_misspecify$beta0_U_SARS_AngToSARS_COV2),
                                                                                 beta_U_SARS_AngToSARS_COV2 = mean(samples_hmc_misspecify$beta_U_SARS_AngToSARS_COV2),
                                                                                 beta0_SARS_COV2ToACE2 = mean(samples_hmc_misspecify$beta0_SARS_COV2ToACE2),
                                                                                 beta_SARS_COV2ToACE2 = mean(samples_hmc_misspecify$beta_SARS_COV2ToACE2),
                                                                                 beta0_ACE2_and_U_SARS_Ang_ToAng = mean(samples_hmc_misspecify$beta0_ACE2_and_U_SARS_Ang_ToAng),
                                                                                 beta_ACE2ToAng = mean(samples_hmc_misspecify$beta_ACE2ToAng),
                                                                                 beta_U_SARS_AngToAng = mean(samples_hmc_misspecify$beta_U_SARS_AngToAng),
                                                                                 beta0_AngToAGTR1 = mean(samples_hmc_misspecify$beta0_AngToAGTR1),
                                                                                 beta_AngToAGTR1 = mean(samples_hmc_misspecify$beta_AngToAGTR1),
                                                                                 mu_U_ADAM17_Sil6r = mean(samples_hmc_misspecify$mu_U_ADAM17_Sil6r),
                                                                                 sigma_U_ADAM17_Sil6r = mean(samples_hmc_misspecify$sigma_U_ADAM17_Sil6r),
                                                                                 beta0_AGTR1_UToADAM17 = mean(samples_hmc_misspecify$beta0_AGTR1_UToADAM17),
                                                                                 beta_AGTR1ToADAM17 = mean(samples_hmc_misspecify$beta_AGTR1ToADAM17),
                                                                                 mean(samples_hmc_misspecify$beta_U_ADAM17_Sil6rToADAM17),
                                                                                 mean(samples_hmc_misspecify$mu_Toci),
                                                                                 mean(samples_hmc_misspecify$sigma_Toci),
                                                                                 mean(samples_hmc_misspecify$beta0_ADAM17_U_TociToSil6r),
                                                                                 mean(samples_hmc_misspecify$beta_ADAM17ToSil6r),
                                                                                 mean(samples_hmc_misspecify$beta_UToSil6r),
                                                                                 mean(samples_hmc_misspecify$beta_TociToSil6r),
                                                                                 mean(samples_hmc_misspecify$mu_U_EGF_EGFR),
                                                                                 mean(samples_hmc_misspecify$sigma_U_EGF_EGFR),
                                                                                 mean(samples_hmc_misspecify$beta0_ADAM17_UToEGF),
                                                                                 mean(samples_hmc_misspecify$beta_ADAM17ToEGF),
                                                                                 mean(samples_hmc_misspecify$beta_UToEGF),
                                                                                 mean(samples_hmc_misspecify$mu_U_EGFR_TNF),
                                                                                 mean(samples_hmc_misspecify$sigma_U_EGFR_TNF),
                                                                                 mean(samples_hmc_misspecify$beta0_ADAM17_UToTNF),
                                                                                 mean(samples_hmc_misspecify$beta_ADAM17ToTNF),
                                                                                 mean(samples_hmc_misspecify$beta_UToTNF),
                                                                                 mean(samples_hmc_misspecify$mu_U_EGFR_IL6STAT3),
                                                                                 mean(samples_hmc_misspecify$sigma_U_EGFR_IL6STAT3),
                                                                                 mean(samples_hmc_misspecify$beta0_EGF_3U),
                                                                                 mean(samples_hmc_misspecify$beta_EGFToEGFR),
                                                                                 mean(samples_hmc_misspecify$beta_U1ToEGFR),
                                                                                 mean(samples_hmc_misspecify$beta_U2ToEGFR),
                                                                                 mean(samples_hmc_misspecify$beta_U3ToEGFR),
                                                                                 beta_GefiToEGFR = mean(samples_hmc_misspecify$beta_GefiToEGFR),
                                                                                 mean(samples_hmc_misspecify$mu_U_PRR_NFKB),
                                                                                 mean(samples_hmc_misspecify$sigma_U_PRR_NFKB),
                                                                                 mean(samples_hmc_misspecify$beta0_SARS_UPRR),
                                                                                 mean(samples_hmc_misspecify$beta_SARS_COV2ToPRR),
                                                                                 mean(samples_hmc_misspecify$beta_UToPRR),
                                                                                 mean(samples_hmc_misspecify$beta0_PRR_U_EGFR_TNFToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_PRRToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_UToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_EGFRToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta_TNFToNFKB),
                                                                                 mean(samples_hmc_misspecify$beta0_NFKB_IL6STSTToIL6STAT3),
                                                                                 mean(samples_hmc_misspecify$beta_UToIL6STAT3),
                                                                                 mean(samples_hmc_misspecify$beta_Sil6rToIL6STAT3),
                                                                                 mean(samples_hmc_misspecify$beta0_NFKB_IL6STATToIL6AMP),
                                                                                 mean(samples_hmc_misspecify$beta_NFKBToIL6AMP),
                                                                                 mean(samples_hmc_misspecify$beta_IL6STAT3ToIL6AMP),
                                                                                 mean(samples_hmc_misspecify$beta0_IL6AMPTocytok),
                                                                                 beta_IL6AMPTocytok = mean(samples_hmc_misspecify$beta_IL6AMPTocytok),
                                                                                 mu_Gefi = mean(samples_hmc_misspecify$mu_Gefi),
                                                                                 sigma_Gefi = mean(samples_hmc_misspecify$sigma_Gefi),
                                                                                 seed = seed, data_count = data_count
    )
    means_hmc_misspecify_egfr <- c(means_hmc_misspecify_egfr,abs(mean(estimated_y_hmc_list_misspecify_egfr[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list_egfr[[data_count]]$cytok)))
    means_hmc_misspecify_sil6r <- c(means_hmc_misspecify_sil6r,abs(mean(estimated_y_hmc_list_misspecify_sil6r[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list_sil6r[[data_count]]$cytok)))
    print("means_hmc_misspecify_egfr")
    print(means_hmc_misspecify_egfr)
    print("means_hmc_misspecify_sil6r")
    print(means_hmc_misspecify_sil6r)
    
  }
  means_hmc_list_misspecify_egfr[[paste0("num_data_points_",num_data_points)]] <- means_hmc_misspecify_egfr
  means_hmc_list_misspecify_sil6r[[paste0("num_data_points_",num_data_points)]] <- means_hmc_misspecify_sil6r
  print("means_hmc_list_misspecify_egfr is:")
  print(means_hmc_list_misspecify_egfr)
  print("means_hmc_list_misspecify_sil6r is:")
  print(means_hmc_list_misspecify_sil6r)
  means_hmc_misspecify_egfr <- c()
  means_hmc_misspecify_sil6r <- c()
}
saveRDS(means_hmc_list_misspecify_egfr,file = "data/Case3_Covid/output/means_hmc_list_misspecify_Case3_egfr.RData")
saveRDS(means_hmc_list_misspecify_sil6r,file = "data/Case3_Covid/output/means_hmc_list_misspecify_Case3_sil6r.RData")
```



# Plug in estimator

In this section we want to compare our approach with the plug-in estimator. We have to construct a parametric model for the conditional distributions that appear in the formula of an identifying functional of a causal effect. For case study 4, the do-calculus based formula is as follows:

$$
P(cytok | do(sil6r = 20)) = \sum_{ADAM17, AGTR1} P(cytoksil6r,ADAM17,AGTR1) P(ADAM17|AGTR1)P(AGTR1) \\
P(cytok | do(EGFR = 20)) = \sum_{AGTR1,IL6STAT3,TNF} P(cytokEGFR,AGTR1,IL6STAT3,TNF)P(AGTR1,IL6STAT3,TNF) \\
= \sum_{AGTR1,IL6STAT3,TNF} P(cytokEGFR,AGTR1,IL6STAT3,TNF)P(IL6STAT3 | AGTR1 ,TNF) P(TNF |AGTR1) P(AGTR1)
$$

The Stan model is as follows:

```{r}
model_str_covid_plug_in_sil6r <- "
    data {
        int D;
        vector[D] AGTR1;
        vector[D] ADAM17;
        vector[D] Sil6r;
        int<lower=0,upper=1> cytok[D];
    }
    parameters {
       real<lower=0> mu_AGTR1; 
       real<lower=0> sigma_AGTR1;
       real beta0_ADAM17;
       real<lower=0> beta_AGTR1ToADAM17;
       real beta0_cytok;
       real<lower=0> beta_Sil6rTocytok;
       real<lower=0> beta_ADAM17Tocytok;
       real<lower=0> beta_AGTR1Tocytok;
       
    }
    transformed parameters {
      vector[D] ADAM17_loc;
      for (i in 1:D){
        ADAM17_loc[i] = 100 / (1 + exp(-beta0_ADAM17 - AGTR1[i] * beta_AGTR1ToADAM17));
      }
    }
    model {
        mu_AGTR1 ~ normal(79, 1); 
        sigma_AGTR1 ~ normal(11, 1); 
        beta0_ADAM17 ~ normal(0,10);
        beta_AGTR1ToADAM17 ~ normal(0,10);
        beta0_cytok ~ normal(0,10);
        beta_Sil6rTocytok ~ normal(0,10);
        beta_ADAM17Tocytok ~ normal(0,10);
        beta_AGTR1Tocytok ~ normal(0,10);
        //
        AGTR1 ~ normal(mu_AGTR1,sigma_AGTR1);
        ADAM17 ~ normal(ADAM17_loc,8.7);
        for(i in 1:D) {
          cytok[i] ~ bernoulli_logit(beta0_cytok + Sil6r[i] * beta_Sil6rTocytok + ADAM17[i] * beta_ADAM17Tocytok + AGTR1[i] * beta_AGTR1Tocytok);
        }
    }
"
```

```{r, message=FALSE, warning=FALSE}
mod_plug_in_sil6r <- rstan::stan_model(model_code = model_str_covid_plug_in_sil6r)
```

```{r}
model_str_covid_plug_in_egfr <- "
    data {
        int D;
        vector[D] AGTR1;
        vector[D] TNF;
        vector[D] IL6STAT3;
        vector[D] EGFR;
        int<lower=0,upper=1> cytok[D];
    }
    parameters {
       real<lower=0> mu_AGTR1; 
       real<lower=0> sigma_AGTR1;
       real beta0_TNF;
       real<lower=0> beta_AGTR1ToTNF;
       real beta0_IL6STAT3;
       real<lower=0> beta_TNFToIL6STAT3;
       real<lower=0> beta_AGTR1ToIL6STAT3;
       
       real beta0_cytok;
       real<lower=0> beta_TNFTocytok;
       real<lower=0> beta_IL6STAT3Tocytok;
       real<lower=0> beta_AGTR1Tocytok;
       real<lower=0> beta_EGFRTocytok;
       
    }
    transformed parameters {
      vector[D] TNF_loc;
      vector[D] IL6STAT3_loc;
      for (i in 1:D){
        TNF_loc[i] = 100 / (1 + exp(-beta0_TNF - AGTR1[i] * beta_AGTR1ToTNF));
        IL6STAT3_loc[i] = 100 / (1 + exp(-beta0_IL6STAT3 - AGTR1[i] * beta_AGTR1ToIL6STAT3 - TNF[i] * beta_TNFToIL6STAT3));
      }
    }
    model {
        mu_AGTR1 ~ normal(79, 1); 
        sigma_AGTR1 ~ normal(11, 1); 
        beta0_TNF ~ normal(0,10);
        beta_AGTR1ToTNF ~ normal(0,10);
        beta0_IL6STAT3 ~ normal(0,10);
        beta_TNFToIL6STAT3 ~ normal(0,10);
        beta_AGTR1ToIL6STAT3 ~ normal(0,10);
        beta0_cytok ~ normal(0,10);
        beta_TNFTocytok ~ normal(0,10);
        beta_IL6STAT3Tocytok ~ normal(0,10);
        beta_AGTR1Tocytok ~ normal(0,10);
        beta_EGFRTocytok ~ normal(0,10);
        //
        AGTR1 ~ normal(mu_AGTR1,sigma_AGTR1);
        TNF ~ normal(TNF_loc,11);
        IL6STAT3 ~ normal(IL6STAT3_loc,21);
        for(i in 1:D) {
          cytok[i] ~ bernoulli_logit(beta0_cytok + IL6STAT3[i] * beta_IL6STAT3Tocytok + TNF[i] * beta_TNFTocytok + AGTR1[i] * beta_AGTR1Tocytok + EGFR[i] * beta_EGFRTocytok);
        }
    }
"
```

```{r, message=FALSE, warning=FALSE}
mod_plug_in_egfr <- rstan::stan_model(model_code = model_str_covid_plug_in_egfr)
```

## Mutilated model

```{r}
num_samples = 1000
mutilated_model_plug_in_sil6r <- function(mu_AGTR1, sigma_AGTR1,
                                    beta0_ADAM17, beta_AGTR1ToADAM17,
                                    beta0_cytok, beta_Sil6rTocytok, beta_ADAM17Tocytok, beta_AGTR1Tocytok, seed, data_count
) {
    set.seed(seed)
    AGTR1_1 = rnorm(num_samples, mu_AGTR1, sigma_AGTR1)
    ADAM17_1 = rnorm(num_samples, 100 / (1 + exp(-beta0_ADAM17 - AGTR1_1 * beta_AGTR1ToADAM17)), sqrt(var(ADAM17)))
    Sil6r_1 = rep(20, num_samples)
    p_cytok = 1 / (1 + exp(-beta0_cytok - Sil6r_1 * beta_Sil6rTocytok - ADAM17_1 * beta_ADAM17Tocytok - AGTR1_1 * beta_AGTR1Tocytok))
    cytok_1 = rbinom(num_samples,size=1, prob=p_cytok)
    return(cytok_1)
}
```

```{r}
num_samples = 1000
mutilated_model_plug_in_egfr <- function(mu_AGTR1, sigma_AGTR1,
                                         beta0_TNF, beta_AGTR1ToTNF,
                                         beta0_IL6STAT3, beta_TNFToIL6STAT3, beta_AGTR1ToIL6STAT3,
                                         beta0_cytok, beta_TNFTocytok, beta_IL6STAT3Tocytok, beta_AGTR1Tocytok, beta_EGFRTocytok,
                                         seed, data_count
) {
    set.seed(seed)
    AGTR1_1 = rnorm(num_samples, mu_AGTR1, sigma_AGTR1)
    TNF_1 = rnorm(num_samples, 100 / (1 + exp(-beta0_TNF - AGTR1_1 * beta_AGTR1ToTNF)), sqrt(var(obs_data_list[[data_count]]$TNF)))
    EGFR_1 = rep(20, num_samples)
    IL6STAT3_1 = rnorm(num_samples, 100 / (1 + exp(-beta0_IL6STAT3 - AGTR1_1 * beta_AGTR1ToIL6STAT3 - TNF_1 * beta_TNFToIL6STAT3)), sqrt(var(obs_data_list[[data_count]]$IL6STAT3)))
    p_cytok = 1 / (1 + exp(-beta0_cytok - TNF_1 * beta_TNFTocytok - IL6STAT3_1 * beta_IL6STAT3Tocytok - AGTR1_1 * beta_AGTR1Tocytok - EGFR_1 * beta_EGFRTocytok))
    cytok_1 = rbinom(num_samples,size=1, prob=p_cytok)
    return(cytok_1)
}
```


```{r}
seed = 5
estimated_y_hmc_list_plug_in <- rep(list(list()), K)
hmc_fit_list_plug_in <- rep(list(list()), K)
means_hmc_plug_in <- c()
means_hmc_list_plug_in <- list()

for (num_data_points in ndp) {
  print("num_data_points is:")
  print(num_data_points)
  for (data_count in 1:K) {
    print("data_count is:")
    print(data_count)
    data_list <- list(D=num_data_points
                  ,AGTR1 = obs_data_list[[data_count]]$AGTR1[1:num_data_points]
                  ,ADAM17 = obs_data_list[[data_count]]$ADAM17[1:num_data_points]
                  ,Sil6r = obs_data_list[[data_count]]$Sil6r[1:num_data_points]
                  ,cytok = obs_data_list[[data_count]]$cytok[1:num_data_points]
                  )
 
    hmc_fit_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]] <- rstan::sampling(mod_plug_in_sil6r, data=data_list, chains = 2, iter = 3000, warmup = 1500, seed = 1, control = list(max_treedepth = 15))
    
    samples_hmc_plug_in <- rstan::extract(hmc_fit_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]], c("mu_AGTR1", "sigma_AGTR1",
                                                                                "beta0_ADAM17", "beta_AGTR1ToADAM17",
                                                                                "beta0_cytok", "beta_Sil6rTocytok", "beta_ADAM17Tocytok", "beta_AGTR1Tocytok"))
    
    estimated_y_hmc_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model_plug_in_sil6r(mu_AGTR1 = mean(samples_hmc_plug_in$mu_AGTR1),
                                                                           sigma_AGTR1 = mean(samples_hmc_plug_in$sigma_AGTR1),
                                                                           beta0_ADAM17 = mean(samples_hmc_plug_in$beta0_ADAM17),
                                                                           beta_AGTR1ToADAM17 = mean(samples_hmc_plug_in$beta_AGTR1ToADAM17),
                                                                           beta0_cytok = mean(samples_hmc_plug_in$beta0_cytok),
                                                                           beta_Sil6rTocytok = mean(samples_hmc_plug_in$beta_Sil6rTocytok),
                                                                           beta_ADAM17Tocytok = mean(samples_hmc_plug_in$beta_ADAM17Tocytok),
                                                                           beta_AGTR1Tocytok = mean(samples_hmc_plug_in$beta_AGTR1Tocytok),
                                                                           seed = seed, data_count = data_count
    )
    means_hmc_plug_in <- c(means_hmc_plug_in,abs(mean(estimated_y_hmc_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list_sil6r[[data_count]]$cytok)))
    
  }
  means_hmc_list_plug_in[[paste0("num_data_points_",num_data_points)]] <- means_hmc_plug_in
  means_hmc_plug_in <- c()
}
saveRDS(hmc_fit_list_plug_in, file = "data/Case3_Covid/output/hmc_fit_list_plug_in_Case3_sil6r.RData")
saveRDS(means_hmc_list_plug_in, file = "data/Case3_Covid/output/means_hmc_list_plug_in_Case3_sil6r.RData")
```

```{r}
seed = 5
estimated_y_hmc_list_plug_in <- rep(list(list()), K)
hmc_fit_list_plug_in <- rep(list(list()), K)
means_hmc_plug_in <- c()
means_hmc_list_plug_in <- list()

for (num_data_points in ndp) {
  print("num_data_points is:")
  print(num_data_points)
  for (data_count in 1:K) {
    print("data_count is:")
    print(data_count)
    data_list <- list(D=num_data_points
                  ,AGTR1 = obs_data_list[[data_count]]$AGTR1[1:num_data_points]
                  ,TNF = obs_data_list[[data_count]]$TNF[1:num_data_points]
                  ,IL6STAT3 = obs_data_list[[data_count]]$IL6STAT3[1:num_data_points]
                  ,EGFR = obs_data_list[[data_count]]$EGFR[1:num_data_points]
                  ,cytok = obs_data_list[[data_count]]$cytok[1:num_data_points]
                  )
    hmc_fit_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]] <- rstan::sampling(mod_plug_in_egfr, data=data_list, chains = 2, iter = 3000, warmup = 1500, seed = 1, control = list(max_treedepth = 15))
    
    samples_hmc_plug_in <- rstan::extract(hmc_fit_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]], c("mu_AGTR1", "sigma_AGTR1",
                                                                                "beta0_TNF", "beta_AGTR1ToTNF",
                                                                                "beta0_IL6STAT3", "beta_TNFToIL6STAT3", "beta_AGTR1ToIL6STAT3",
                                                                                "beta0_cytok", "beta_TNFTocytok", "beta_IL6STAT3Tocytok", "beta_AGTR1Tocytok", "beta_EGFRTocytok"))
  
    estimated_y_hmc_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model_plug_in_egfr(mu_AGTR1 = mean(samples_hmc_plug_in$mu_AGTR1),
                                                                           sigma_AGTR1 = mean(samples_hmc_plug_in$sigma_AGTR1),
                                                                           beta0_TNF = mean(samples_hmc_plug_in$beta0_TNF),
                                                                           beta_AGTR1ToTNF = mean(samples_hmc_plug_in$beta_AGTR1ToTNF),
                                                                           beta0_IL6STAT3 = mean(samples_hmc_plug_in$beta0_IL6STAT3),
                                                                           beta_TNFToIL6STAT3 = mean(samples_hmc_plug_in$beta_TNFToIL6STAT3),
                                                                           beta_AGTR1ToIL6STAT3 = mean(samples_hmc_plug_in$beta_AGTR1ToIL6STAT3),
                                                                           beta0_cytok = mean(samples_hmc_plug_in$beta0_cytok),
                                                                           beta_TNFTocytok = mean(samples_hmc_plug_in$beta_TNFTocytok),
                                                                           beta_IL6STAT3Tocytok = mean(samples_hmc_plug_in$beta_IL6STAT3Tocytok),
                                                                           beta_AGTR1Tocytok = mean(samples_hmc_plug_in$beta_AGTR1Tocytok),
                                                                           beta_EGFRTocytok = mean(samples_hmc_plug_in$beta_EGFRTocytok),
                                                                           seed = seed, data_count = data_count
    )
    means_hmc_plug_in <- c(means_hmc_plug_in,abs(mean(estimated_y_hmc_list_plug_in[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list_egfr[[data_count]]$cytok)))
    
  }
  means_hmc_list_plug_in[[paste0("num_data_points_",num_data_points)]] <- means_hmc_plug_in
  means_hmc_plug_in <- c()
}
saveRDS(hmc_fit_list_plug_in, file = "data/Case3_Covid/output/hmc_fit_list_plug_in_Case3_egfr.RData")
saveRDS(means_hmc_list_plug_in, file = "data/Case3_Covid/output/means_hmc_list_plug_in_Case3_egfr.RData")
```
