---
title: "Example 2"
author: "Sara Taheri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, warning=FALSE, message=FALSE, include=FALSE}
# theta_M and theta_MY are identifiable: seed: 22, hmc_seed : 10
# seed: 60
source("training_data_and_true_params.R", local = knitr::knit_global())
options(mc.cores = parallel::detectCores())
rstan_options(auto_write = TRUE)
```


**Note:** First run ```trainind_data_and_true_params.R``` from the R folder.

# Estimating the parameters of model when there is no hidden confounder

```{r}
round(mu,2)
round(theta_UX,2)
round(theta_XM,2)
round(theta_UY,2)
round(theta_MY,2)
```


```{r}
Sigma_uu
Sigma_xx
Sigma_mm
Sigma_yy
```


## Stan model


The Stan model is in vignette under the name of ```model_str.stan```. Let's complie the model:

```{r}
mod_with_hidden_confounder <- rstan::stan_model("model_str.stan")
```

## HMC in presecne of hidden confounder
 
let's use hmc approach.

```{r, echo = FALSE}
data_list_with_hidden_confounder <- list(L=L, D=D, N =N, x = x_train, m = m_train, y = y_train)
#If you get this error (Cluster setup failed. 2 of 2 workers failed to connect.) run these lines:
# if (Sys.getenv("RSTUDIO") == "1" && !nzchar(Sys.getenv("RSTUDIO_TERM")) &&
#     Sys.info()["sysname"] == "Darwin") {
#   parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
# }
hmc_fit_with_hidden_confounder <- rstan::sampling(mod_with_hidden_confounder, data=data_list_with_hidden_confounder, chains = 2, iter = 3000, warmup = 1500, seed = 7, control = list(max_treedepth = 15)) #seed 7, change to 10
```


```{r}
stan_trace(pars = "mu", hmc_fit_with_hidden_confounder)
```

```{r}
stan_trace(pars = "u_scale", hmc_fit_with_hidden_confounder)
```

```{r }
stan_trace(pars = "theta_UX", hmc_fit_with_hidden_confounder)
```

```{r}
stan_trace(pars = "theta_XM", hmc_fit_with_hidden_confounder)
```

```{r}
stan_trace(pars = "theta_UY", hmc_fit_with_hidden_confounder)
```

```{r }
stan_trace(pars = "theta_MY", hmc_fit_with_hidden_confounder)
```

Now let's extract the samples:

```{r}
#hmc_fit_with_hidden_confounder <- readRDS(file = "hmc_fit_whc_D100_N1_L1_parseed20_hmcseed10.RData")
samples_whc <- rstan::extract(hmc_fit_with_hidden_confounder, c("theta_UX", "theta_XM", "theta_UY", "theta_MY", "mu","u_scale"))

print("mu")
round(colMeans(samples_whc$mu),2)
round(mu,2)
print("theta_UX")
round(colMeans(samples_whc$theta_UX),2)
round(theta_UX,2)
print("theta_XM")
round(colMeans(samples_whc$theta_XM),2)
round(theta_XM,2)
print("theta_UY")
round(colMeans(samples_whc$theta_UY),2)
round(theta_UY,2)
print("theta_MY")
round(colMeans(samples_whc$theta_MY),2)
round(theta_MY,2)
print("u_scale")
round(colMeans(samples_whc$u_scale),2)
round(Sigma_uu,2)
```

$\theta_XM$ and $\theta_MY$ parameters are estimated correctly! 

```{r}
#saveRDS(hmc_fit_with_hidden_confounder, "hmc_fit_whc_D100_N1_L1_parseed20_hmcseed10.RData")
```



# Consistency plots

# True distribution

Let's calculate the true mean of $P(Y | do(X = x))$ distribution,

$$P(Y | do(X = x)) \text{equal in dist} N(x \theta_{XM} \theta_{MY} + \mu \theta_{UY}, \Sigma_{YY|do(x)}) = N(x \theta_{XM} \theta_{MY} + \mu \theta_{UY}, \theta_MY^T \theta_{MY} + \theta_{UY}^T \Sigma_{UU} \theta_{UY} + 1)$$

```{r}
set.seed(seed)
# generate x1
x = mvtnorm::rmvnorm(n = 1, mean = mu %*% theta_UX, sigma = Sigma_xx)
mean_y_given_do_x = x %*% theta_XM %*% theta_MY + mu %*% theta_UY
var_y_given_do_x_alex = t(theta_MY) %*% theta_MY + t(theta_UY) %*% Sigma_uu %*% theta_UY + 1
std_y_given_do_x_alex = sqrt(var_y_given_do_x_alex[1,1])
mean_y_given_do_x
```

```{r}
# one dimensional
mutilated_model <- function(mu, theta_XM, theta_UY, theta_MY, x, num_samples = 1000, seed = 10) {
  set.seed(seed)
  u = mvtnorm::rmvnorm(n = num_samples, mean = mu , sigma = diag(L)) 
  x = x
  m = matrix(x, nrow = num_samples, ncol = N, byrow = TRUE) %*% theta_XM + matrix(rnorm(n = num_samples, mean = 0, sd = 1), nrow = num_samples, ncol = 1)
  y = matrix(m, nrow = num_samples, ncol = 1) %*% theta_MY + matrix(u, nrow = num_samples, ncol = L) %*% theta_UY + matrix(rnorm(n = num_samples, mean = 0, sd = 1), nrow = num_samples, ncol = 1)
  return(y)
  #return(density(y))
}
```


### HMC estimated distribution of $P(Y | do(X = x))$ with hidden confounder

```{r}
# everything one dimension
hmc_fit_whc_D10_N1_L1_parseed20_hmcseed10 <- readRDS("hmc_fit_whc_D10_N1_L1_parseed20_hmcseed10.RData")
hmc_fit_whc_D50_N1_L1_parseed20_hmcseed10 <- readRDS("hmc_fit_whc_D50_N1_L1_parseed20_hmcseed10.RData")
hmc_fit_whc_D100_N1_L1_parseed20_hmcseed10 <- readRDS("hmc_fit_whc_D100_N1_L1_parseed20_hmcseed10.RData")
samples10_hid <- rstan::extract(hmc_fit_whc_D10_N1_L1_parseed20_hmcseed10, c("theta_UX", "theta_XM", "theta_UY", "theta_MY", "mu", "u_scale"))
samples50_hid <- rstan::extract(hmc_fit_whc_D50_N1_L1_parseed20_hmcseed10, c("theta_UX", "theta_XM", "theta_UY", "theta_MY", "mu", "u_scale"))
samples100_hid <- rstan::extract(hmc_fit_whc_D100_N1_L1_parseed20_hmcseed10, c("theta_UX", "theta_XM", "theta_UY", "theta_MY", "mu", "u_scale"))
```


```{r}
indexes = sample(length(samples100_hid$mu[,,1]), 100, replace = FALSE)
y_grey = list()
y_blue = list()
y_green = list()
mu_eta = c()
for (i in 1:length(indexes)) {
  j = indexes[i]
  y_grey[[i]] = mutilated_model(mu = samples10_hid$mu[j],
                                theta_XM = samples10_hid$theta_XM[j],
                                theta_UY = samples10_hid$theta_UY[j],
                                theta_MY = samples10_hid$theta_MY[j],
                                x = x)
  y_blue[[i]] = mutilated_model(mu = samples50_hid$mu[j],
                                theta_XM = samples50_hid$theta_XM[j],
                                theta_UY = samples50_hid$theta_UY[j],
                                theta_MY = samples50_hid$theta_MY[j],
                                x = x
  )
  y_green[[i]] = mutilated_model(mu = samples100_hid$mu[j],
                                theta_XM = samples100_hid$theta_XM[j],
                                theta_UY = samples100_hid$theta_UY[j],
                                theta_MY = samples100_hid$theta_MY[j],
                                x = x)
  #mu*theta_UY
  #mu_eta = c(mu_eta,t(as.matrix(unlist(c(df_whc(samples200_hid)$df_mu_whc[j,])))) %*% matrix(unlist(df_whc(samples200_hid)$df_eta_whc[j,]), nrow = L, ncol = 1))
}
```

```{r}
#png(file="example2Density.png",width=600, height=350)
#par(mfrow = c(3,1))
x_true_density <- seq(-160,-50, length = 1000)
y_true_density <- dnorm(x_true_density, mean = mean_y_given_do_x, sd = std_y_given_do_x_alex)

png(file="example2Density1.png",width=600, height=350)
plot(x = x_true_density, y = y_true_density, lwd = 0.6, col = "black", xlab = "# data points used for training = 10", ylab = "", cex.lab = 3, cex.axis = 2.5, main = "P(Y|do(x'))", cex.main = 3, ylim = c(0,0.08))
title(ylab="", line=2.35, cex.lab=2.5)
for (i in 1:length(indexes)) {
  lines(density(y_grey[[i]]), lwd = 0.6, col = "grey")
}
dev.off()

png(file="example2Density2.png",width=600, height=350)
plot(x = x_true_density, y = y_true_density, lwd = 0.6, col = "black", xlab = "# data points used for training = 50", ylab = "", cex.lab = 3, cex.axis = 2.5, main = "P(Y|do(x'))", cex.main = 3, ylim = c(0,0.08))
title(ylab="", line=2.35, cex.lab=2.5)
for (i in 1:length(indexes)) {
  lines(density(y_blue[[i]]), lwd = 0.6, col = "blue")
}
dev.off()

png(file="example2Density3.png",width=600, height=350)
plot(x = x_true_density, y = y_true_density, lwd = 0.6, col = "black", xlab = "# data points used for training = 100", ylab = "", cex.lab = 3, cex.axis = 2.5, main = "P(Y|do(x'))", cex.main = 3, ylim = c(0,0.08))
title(ylab="", line=2.35, cex.lab=2.5)
for (i in 1:length(indexes)) {
  lines(density(y_green[[i]]), lwd = 0.6, col = "green")
}
dev.off()

```




