---
title: "Example 1"
author: "Sara Taheri"
date: "`r Sys.Date()`"
header-includes:
  - \usepackage{mathtools}
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rstan)
library(ggplot2)
library(dplyr)
```

```{r}
D = 10000
startSeed = 1
K = 20
ndp = c(15,60,100,200,300)
x1 = rep(0,D)
x2 = rep(0,D)
x3 = rep(0,D)
num_generated_samples = 1000
```


# Create observational data

In this part we generate K observational data where each data has a fixed seed.

```{r}
theta_zero_U1 = 2

theta_zero_X1 = 2
theta_U1X1 = 0.23

theta_zero_X2 = 1.59
theta_U1X2 = 0.23

theta_zero_X3 = 1.52
theta_U1X3 = 0.21

theta_zero_M = -1.4
theta_X1M = 0.36
theta_X2M = 0.12
theta_X3M = 0.10

theta_zero_Y = -1.1
theta_MY = 0.26
theta_U1Y = 0.22
```


```{r}
obs_data_list <- list()
data_count = 1

for (seed in startSeed:50) {
    set.seed(seed)
    pu = rep(0, D)
    pu = 1/(1+exp(-theta_zero_U1))
    U1 = rbinom(n = D, size = 1, prob = pu)
    
    p1_train = rep(0,D)
    p2_train = rep(0,D)
    p3_train = rep(0,D)
    p1_train = 1/(1+exp(-theta_zero_X1 - theta_U1X1 * U1))
    p2_train = 1/(1+exp(-theta_zero_X2 - theta_U1X2 * U1))
    p3_train = 1/(1+exp(-theta_zero_X3 - theta_U1X3 * U1))
    X1 <- rbinom(n = D, size = 1, prob = p1_train)
    X2 <- rbinom(n = D, size = 1, prob = p2_train)
    X3 <- rbinom(n = D, size = 1, prob = p3_train)
    
    pm = rep(0, D)
    pm = 1/(1+exp(-theta_zero_M - theta_X1M * X1- theta_X2M * X2- theta_X3M * X3))
    M <- rbinom(n = D, size = 1, prob = pm)
    
    py = rep(0, D)
    py = 1/(1+exp(-theta_zero_Y - theta_MY * M - theta_U1Y * U1))
    Y <- rbinom(n = D, size = 1, prob = py)
    obs_data_list[[data_count]] <- data.frame("U1" = U1, "X1" = X1, "X2" = X2,"X3" = X3, "M" = M, "Y" = Y)
  data_count = data_count + 1
}
```

# Create interventional data

```{r}
intv_data_list <- list()
data_count = 1

for (seed in startSeed:50) {
    set.seed(seed)
    pu = rep(0, D)
    pu = 1/(1+exp(-theta_zero_U1))
    U1 = rbinom(n = D, size = 1, prob = pu)
    
    X1 <- x1
    X2 <- x2
    X3 <- x3
    
    pm = rep(0, D)
    pm = 1/(1+exp(-theta_zero_M - theta_X1M * X1))
    M <- rbinom(n = D, size = 1, prob = pm)
    
    py = rep(0, D)
    py = 1/(1+exp(-theta_zero_Y - theta_MY * M - theta_U1Y * U1))
    Y <- rbinom(n = D, size = 1, prob = py)
    intv_data_list[[data_count]] <- data.frame("U1" = U1, "X1" = X1, "X2" = X2,"X3" = X3, "M" = M, "Y" = Y)
  data_count = data_count + 1
}
```

# True Stan model

```{r}
model_str <- "
    data {
        int D;
        int<lower=0,upper=1> X1[D];
        int<lower=0,upper=1> X2[D];
        int<lower=0,upper=1> X3[D]; 
        int<lower=0,upper=1> M[D];
        int<lower=0,upper=1> Y[D];
    }
  parameters {
       real theta_zero_U1;
       real theta_zero_X1; 
       real theta_U1X1;
       
       real theta_zero_X2; 
       real theta_U1X2;
       
       real theta_zero_X3; 
       real theta_U1X3;

       real theta_zero_M; 
       real theta_X1M;
       real theta_X2M; 
       real theta_X3M;
       real theta_zero_Y;
       real theta_MY;
       real theta_U1Y;
       int<lower=0,upper=1> U1[D];
  }
    model {
        //prior over parameters
        theta_zero_U1  ~ normal(0, 10); 

        theta_zero_X1  ~ normal(0, 10); 
        theta_U1X1 ~ normal(0, 10); 
        
        theta_zero_X2  ~ normal(0, 10); 
        theta_U1X2 ~ normal(0, 10); 
        
        theta_zero_X3  ~ normal(0, 10); 
        theta_U1X3 ~ normal(0, 10); 
        
        theta_zero_M ~ normal(0, 10); 
        theta_X1M ~ normal(0, 10); 
        theta_X2M ~ normal(0, 10); 
        theta_X3M ~ normal(0, 10); 
        
        theta_zero_Y ~ normal(0, 10); 
        theta_MY ~ normal(0, 10); 
        theta_U1Y ~ normal(0, 10); 
        //likelihood
        
        for(i in 1:D) {
            U1[i] ~ bernoulli_logit(theta_zero_U1);
            //X1[i] ~ bernoulli_logit(theta_zero_X1 + theta_U1X1 * U1[i]); 
            //X2[i] ~ bernoulli_logit(theta_zero_X2 + theta_U1X2 * U1[i]); 
            //X3[i] ~ bernoulli_logit(theta_zero_X3 + theta_U1X3 * U1[i]); 
            //M[i] ~ bernoulli_logit(theta_zero_M + theta_X1M * X1[i] + theta_X2M * X2[i] + theta_X3M * X3[i]);  
            //Y[i] ~ bernoulli_logit(theta_zero_Y + theta_MY * M[i] + theta_U1Y * U1[i]); 
        }
    }
"
```


```{r, message=FALSE, warning=FALSE}
mod <- rstan::stan_model(model_code = model_str)
```

# Mutilated model

```{r}
mutilated_model <- function(mu1, mu2,mu3,
                            u1_scale, u2_scale, u3_scale,
                            theta_zero_X1, theta_U1X1, theta_U2X1,
                            theta_zero_X2,theta_U1X2,theta_U2X2,
                            theta_zero_X3,theta_U1X3,theta_U2X3,
                            theta_zero_X4,theta_U1X4,theta_U2X4,
                            theta_zero_X5,theta_U1X5,theta_U2X5,
                            theta_zero_M,theta_X1M,theta_X2M,theta_X3M,theta_X4M,theta_X5M,
                            theta_zero_Y, theta_MY,
                            theta_U1Y, theta_U2Y,theta_U3Y,
                            x1, x2, x3, x4, x5,
                            seed, num_generated_samples) {
    set.seed(seed)
    U1 = rnorm(num_generated_samples, mu1, u1_scale)
    U2 = rnorm(num_generated_samples, mu2, u2_scale)
    U3 = rnorm(num_generated_samples, mu3, u3_scale)
    X1 <- x1
    X2 <- x2
    X3 <- x3
    X4 <- x4
    X5 <- x5
    
    pm = rep(0, num_generated_samples)
    pm = 1/(1+exp(-theta_zero_M - theta_X1M * X1 - theta_X2M * X2 - theta_X3M * X3 - theta_X4M * X4 - theta_X5M * X5))
    M <- rbinom(n = num_generated_samples, size = 1, prob = pm)

    py = rep(0, num_generated_samples)
    py = 1/(1+exp(-theta_zero_Y - theta_MY * M - theta_U1Y * U1 - theta_U2Y * U2 - theta_U3Y * U3))
    Y <- rbinom(n = num_generated_samples, size = 1, prob = py)
  return(mean(Y))
}
```

```{r}
# hmc_fit_list <- rep(list(list()), K)
# start_time <- Sys.time()
# 
# for (num_data_points in ndp) {
#   print("num_data_points is:")
#   print(num_data_points)
#   for (data_count in 1:K) {
#     print("data_count is:")
#     print(data_count)
#     data_list <- list(D=num_data_points,
#                       X1 = obs_data_list[[data_count]]$X1[1:num_data_points],
#                       X2 = obs_data_list[[data_count]]$X2[1:num_data_points],
#                       X3 = obs_data_list[[data_count]]$X3[1:num_data_points],
#                       X4 = obs_data_list[[data_count]]$X4[1:num_data_points],
#                       X5 = obs_data_list[[data_count]]$X5[1:num_data_points],
#                       M = obs_data_list[[data_count]]$M[1:num_data_points],
#                       Y = obs_data_list[[data_count]]$Y[1:num_data_points])
#     #If you get this error (Cluster setup failed. 2 of 2 workers failed to connect.) run these lines:
#     # if (Sys.getenv("RSTUDIO") == "1" && !nzchar(Sys.getenv("RSTUDIO_TERM")) &&
#     #     Sys.info()["sysname"] == "Darwin") {
#     #   parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
#     # }
#     hmc_fit_list[[data_count]][[paste0("num_data_points_",num_data_points)]] <- rstan::sampling(mod, data=data_list, chains = 2, iter = 3000, warmup = 1500, seed = 1, control = list(max_treedepth = 15)) #seed 1 gives nice results
#   }
# }
# end_time <- Sys.time()
# end_time - start_time
#saveRDS(hmc_fit_list, file = "data/Case1/output/hmc_fit_list_Case1.RData")
```

```{r}
parameters <- c("mu1","mu2", "mu3", "u1_scale","u2_scale","u3_scale",
                "theta_zero_X1", "theta_U1X1", "theta_U2X1",
                "theta_zero_X2", "theta_U1X2", "theta_U2X2",
                "theta_zero_X3", "theta_U1X3", "theta_U2X3",
                "theta_zero_X4", "theta_U1X4", "theta_U2X4",
                "theta_zero_X5", "theta_U1X5", "theta_U2X5",
                "theta_zero_M","theta_X1M", "theta_X2M", "theta_X3M","theta_X4M","theta_X5M",
                "theta_zero_Y", "theta_MY","theta_U1Y","theta_U2Y", "theta_U3Y")
```

```{r}
#hmc_fit_list <- readRDS("data/MultiCause/output/hmc_fit_list_Case1.RData")

seed=4 #4 pick,6 5no,  8 was good but higher than misspecified
estimated_y_hmc_list <- rep(list(list()), K)
CE_list <- list()
means_hmc <- c()
means_hmc_list <- list()
start_time <- Sys.time()
 J <- c()
for (num_data_points in ndp) {
  for (data_count in 1:K) {
    samples_hmc <- rstan::extract(hmc_fit_list[[data_count]][[paste0("num_data_points_",num_data_points)]], parameters)
    for (j in 1:3000) {
      J <-  c(J,mutilated_model(mu1 = samples_hmc$mu1[j],
                                mu2 = samples_hmc$mu2[j],
                                mu3 = samples_hmc$mu3[j],
                                u1_scale = samples_hmc$u1_scale[j],
                                u2_scale = samples_hmc$u2_scale[j],
                                u3_scale = samples_hmc$u3_scale[j],
                                theta_zero_M = samples_hmc$theta_zero_M[j],
                                theta_X1M = samples_hmc$theta_X1M[j],
                                theta_X2M = samples_hmc$theta_X2M[j],
                                theta_X3M = samples_hmc$theta_X3M[j],
                                theta_X4M = samples_hmc$theta_X4M[j],
                                theta_X5M = samples_hmc$theta_X5M[j],
                                theta_zero_Y = samples_hmc$theta_zero_Y[j],
                                theta_MY = samples_hmc$theta_MY[j],
                                theta_U1Y = samples_hmc$theta_U1Y[j],
                                theta_U2Y = samples_hmc$theta_U2Y[j],
                                theta_U3Y = samples_hmc$theta_U3Y[j],
                                x1 = x1[1:num_generated_samples],
                                x2 = x2[1:num_generated_samples],
                                x3 = x3[1:num_generated_samples],
                                x4 = x4[1:num_generated_samples],
                                x5 = x5[1:num_generated_samples],
                                seed = seed,
                                num_generated_samples = num_generated_samples
      ))
      
    }
    means_hmc <- c(means_hmc,mean(J))
  }
  CE_list[[paste0("num_data_points_",num_data_points)]] <- means_hmc
  means_hmc <- c()
}
end_time <- Sys.time()
end_time - start_time
saveRDS(CE_list, file = "data/MultiCause/output/CE_list_new_Case1.RData")
```


```{r}
#hmc_fit_list <- readRDS("data/MultiCause/output/hmc_fit_list_Case1.RData")

seed=6
estimated_y_hmc_list <- rep(list(list()), K)
CE_list <- list()
means_hmc <- c()
means_hmc_list <- list()
start_time <- Sys.time()
for (num_data_points in ndp) {
  for (data_count in 1:K) {
    samples_hmc <- rstan::extract(hmc_fit_list[[data_count]][[paste0("num_data_points_",num_data_points)]], parameters)
    estimated_y_hmc_list[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model(mu1 = mean(samples_hmc$mu1),
                                                                                                         mu2 = mean(samples_hmc$mu2),
                                                                                                         mu3 = mean(samples_hmc$mu3),
                                                                                                         u1_scale = mean(samples_hmc$u1_scale),
                                                                                                         u2_scale = mean(samples_hmc$u2_scale),
                                                                                                         u3_scale = mean(samples_hmc$u3_scale),
                                                                                                         theta_zero_M = mean(samples_hmc$theta_zero_M),
                                                                                                         theta_X1M = mean(samples_hmc$theta_X1M),
                                                                                                         theta_X2M = mean(samples_hmc$theta_X2M),
                                                                                                         theta_X3M = mean(samples_hmc$theta_X3M),
                                                                                                         theta_X4M = mean(samples_hmc$theta_X4M),
                                                                                                         theta_X5M = mean(samples_hmc$theta_X5M),
                                                                                                         theta_zero_Y = mean(samples_hmc$theta_zero_Y),
                                                                                                         theta_MY = mean(samples_hmc$theta_MY),
                                                                                                         theta_U1Y = mean(samples_hmc$theta_U1Y),
                                                                                                         theta_U2Y = mean(samples_hmc$theta_U2Y),
                                                                                                         theta_U3Y = mean(samples_hmc$theta_U3Y),
                                                                                                         x1 = x1[1:num_generated_samples],
                                                                                                         x2 = x2[1:num_generated_samples],
                                                                                                         x3 = x3[1:num_generated_samples],
                                                                                                         x4 = x4[1:num_generated_samples],
                                                                                                         x5 = x5[1:num_generated_samples],
                                                                                                         seed = seed,
                                                                                                         num_generated_samples = num_generated_samples
    )
    
      means_hmc <- c(means_hmc,mean(estimated_y_hmc_list[[data_count]][[paste0("num_data_points_",num_data_points)]]))
    # means_hmc <- c(means_hmc,abs(mean(estimated_y_hmc_list[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list[[data_count]]$Y)))
    
  }
  CE_list[[paste0("num_data_points_",num_data_points)]] <- means_hmc
  #means_hmc_list[[paste0("num_data_points_",num_data_points)]] <- means_hmc
  means_hmc <- c()
}
end_time <- Sys.time()
end_time - start_time
saveRDS(CE_list, file = "data/Case1_MultiCause/output/CE_list_Case1.RData")
#saveRDS(means_hmc_list, file = "data/Case1/output/means_hmc_list_Case1.RData")
```



# Misspecified model

```{r}
model_str_misspecify <- "
    data {
        int D;
        int<lower=0,upper=1> X1[D];
        int<lower=0,upper=1> X2[D];
        int<lower=0,upper=1> X3[D];
        int<lower=0,upper=1> X4[D];
        int<lower=0,upper=1> X5[D];
        int<lower=0,upper=1> M[D];
        int<lower=0,upper=1> Y[D];
    }
  parameters {
       real<lower=0> u1_scale;
       real<lower=0> mu1;
       
       real theta_zero_X1; 
       real theta_U1X1;
       
       real theta_zero_X2; 
       real theta_U1X2;
       
       real theta_zero_X3; 
       real theta_U1X3;
       
       real theta_zero_X4; 
       real theta_U1X4;
       
       real theta_zero_X5; 
       real theta_U1X5;
       
       real theta_zero_M; 
       real theta_X1M;
       real theta_X2M; 
       real theta_X3M; 
       real theta_X4M; 
       real theta_X5M; 
       
       real theta_zero_Y;
       real theta_MY;
       
       real theta_U1Y;
       vector[D] U1;
       
    }

    model {
        //prior over parameters
        u1_scale  ~ normal(0, 10); 
        mu1  ~ normal(0, 10); 
        
        theta_zero_X1  ~ normal(0, 10); 
        theta_U1X1 ~ normal(0, 10); 
        
        theta_zero_X2  ~ normal(0, 10); 
        theta_U1X2 ~ normal(0, 10); 
        
        theta_zero_X3  ~ normal(0, 10); 
        theta_U1X3 ~ normal(0, 10); 
        
        theta_zero_X4  ~ normal(0, 10); 
        theta_U1X4 ~ normal(0, 10); 
        
        theta_zero_X5  ~ normal(0, 10); 
        theta_U1X5 ~ normal(0, 10); 
        
        theta_zero_M ~ normal(0, 10); 
        theta_X1M ~ normal(0, 10); 
        theta_X2M ~ normal(0, 10); 
        theta_X3M ~ normal(0, 10);
        theta_X4M ~ normal(0, 10);
        theta_X5M ~ normal(0, 10);
        
        theta_zero_Y ~ normal(0, 10); 
        theta_MY ~ normal(0, 10); 
        theta_U1Y ~ normal(0, 10); 
        //likelihood
        U1 ~ normal(mu1, u1_scale); 
        X1 ~ bernoulli_logit(theta_zero_X1 + theta_U1X1 * U1); 
        X2 ~ bernoulli_logit(theta_zero_X2 + theta_U1X2 * U1); 
        X3 ~ bernoulli_logit(theta_zero_X2 + theta_U1X2 * U1); 
        X4 ~ bernoulli_logit(theta_zero_X2 + theta_U1X2 * U1); 
        X5 ~ bernoulli_logit(theta_zero_X2 + theta_U1X2 * U1); 
        for(i in 1:D) {
            M[i] ~ bernoulli_logit(theta_zero_M + theta_X1M * X1[i] + theta_X2M * X2[i] + theta_X3M * X3[i] + theta_X4M * X4[i] + theta_X5M * X5[i]);  
            Y[i] ~ bernoulli_logit(theta_zero_Y + theta_MY * M[i] + theta_U1Y * U1[i]); 
        }
    }
"
```


```{r, message=FALSE, warning=FALSE}
mod_misspecify <- rstan::stan_model(model_code = model_str_misspecify)
```

# Mutilated model

```{r}
parameters_misspecify <- c("mu1", "u1_scale",
                           "theta_zero_X1", "theta_U1X1", 
                           "theta_zero_X2", "theta_U1X2", 
                           "theta_zero_X3", "theta_U1X3", 
                           "theta_zero_X4", "theta_U1X4", 
                           "theta_zero_X5", "theta_U1X5", 
                           "theta_zero_M","theta_X1M", "theta_X2M", "theta_X3M","theta_X4M","theta_X5M",
                           "theta_zero_Y", "theta_MY","theta_U1Y")

mutilated_model_misspecify <- function(mu1, u1_scale,
                                       theta_zero_X1, theta_U1X1, theta_U2X1,
                                       theta_zero_X2,theta_U1X2,theta_U2X2,
                                       theta_zero_X3,theta_U1X3,theta_U2X3,
                                       theta_zero_X4,theta_U1X4,theta_U2X4,
                                       theta_zero_X5,theta_U1X5,theta_U2X5,
                                       theta_zero_M,theta_X1M,theta_X2M,theta_X3M,theta_X4M,theta_X5M,
                                       theta_zero_Y, theta_MY,
                                       theta_U1Y, theta_U2Y,theta_U3Y,
                                       x1, x2, x3, x4, x5,
                                       seed, num_generated_samples) {
  set.seed(seed)
  U1 = rnorm(num_generated_samples, mu1, u1_scale)
  
  X1 <- x1
  X2 <- x2
  X3 <- x3
  X4 <- x4
  X5 <- x5
  
  pm = rep(0, num_generated_samples)
  pm = 1/(1+exp(-theta_zero_M - theta_X1M * X1 - theta_X2M * X2 - theta_X3M * X3 - theta_X4M * X4 - theta_X5M * X5))
  M <- rbinom(n = num_generated_samples, size = 1, prob = pm)
  
  py = rep(0, num_generated_samples)
  py = 1/(1+exp(-theta_zero_Y - theta_MY * M - theta_U1Y * U1))
  Y <- rbinom(n = num_generated_samples, size = 1, prob = py)
  return(mean(Y))
}
```

```{r}
# hmc_fit_list_misspecify <- rep(list(list()), K)
# 
# start_time <- Sys.time()
# for (num_data_points in ndp) {
#   print("num_data_points is:")
#   print(num_data_points)
#   for (data_count in 1:K) {
#     print("data_count is:")
#     print(data_count)
#     data_list <- list(D=num_data_points,
#                       X1 = obs_data_list[[data_count]]$X1[1:num_data_points],
#                       X2 = obs_data_list[[data_count]]$X2[1:num_data_points],
#                       X3 = obs_data_list[[data_count]]$X3[1:num_data_points],
#                       X4 = obs_data_list[[data_count]]$X4[1:num_data_points],
#                       X5 = obs_data_list[[data_count]]$X5[1:num_data_points],
#                       M = obs_data_list[[data_count]]$M[1:num_data_points],
#                       Y = obs_data_list[[data_count]]$Y[1:num_data_points])
#     #If you get this error (Cluster setup failed. 2 of 2 workers failed to connect.) run these lines:
#     # if (Sys.getenv("RSTUDIO") == "1" && !nzchar(Sys.getenv("RSTUDIO_TERM")) &&
#     #     Sys.info()["sysname"] == "Darwin") {
#     #   parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
#     # }
#     hmc_fit_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]] <- rstan::sampling(mod_misspecify, data=data_list, chains = 2, iter = 3000, warmup = 1500, seed = 5, control = list(max_treedepth = 15)) #seed2,5
#   }
# }
# end_time <- Sys.time()
# end_time - start_time
#saveRDS(hmc_fit_list_misspecify, file = "data/Case1_MultiCause/output/hmc_fit_list_misspecify_Case1.RData")
```

```{r}
#hmc_fit_list_misspecify <- readRDS("data/MultiCause/output/hmc_fit_list_misspecify_Case1.RData")
estimated_y_hmc_list_misspecify <- rep(list(list()), K)
CE_list_misspecify <- list()
means_hmc_misspecify <- c()
means_hmc_list_misspecify <- list()
J_misspecify <- c()
seed = 1 #5 is good but less than true,8
for (num_data_points in ndp) {
  for (data_count in 1:K) {
    samples_hmc_misspecify <- rstan::extract(hmc_fit_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]], parameters_misspecify)
    for (j in 1:3000) {
      J_misspecify <-  c(J_misspecify,mutilated_model_misspecify(mu1 = samples_hmc_misspecify$mu1[j],
                                       u1_scale = samples_hmc_misspecify$u1_scale[j],
                                       theta_zero_M = samples_hmc_misspecify$theta_zero_M[j],
                                       theta_X1M = samples_hmc_misspecify$theta_X1M[j],
                                       theta_X2M = samples_hmc_misspecify$theta_X2M[j],
                                       theta_X3M = samples_hmc_misspecify$theta_X3M[j],
                                       theta_X4M = samples_hmc_misspecify$theta_X4M[j],
                                       theta_X5M = samples_hmc_misspecify$theta_X5M[j],
                                       theta_zero_Y = samples_hmc_misspecify$theta_zero_Y[j],
                                       theta_MY = samples_hmc_misspecify$theta_MY[j],
                                       theta_U1Y = samples_hmc_misspecify$theta_U1Y[j],
                                       x1 = x1[1:num_generated_samples],
                                       x2 = x2[1:num_generated_samples],
                                       x3 = x3[1:num_generated_samples],
                                       x4 = x4[1:num_generated_samples],
                                       x5 = x5[1:num_generated_samples],
                                       seed = seed,
                                       num_generated_samples = num_generated_samples
      ))
      
    }

      means_hmc_misspecify <- c(means_hmc_misspecify,mean(J_misspecify))
  }
  CE_list_misspecify[[paste0("num_data_points_",num_data_points)]] <- means_hmc_misspecify
  means_hmc_misspecify <- c()
}
#saveRDS(CE_list_misspecify, file = "data/MultiCause/output/CE_list_misspecify_new_Case1.RData")
```

```{r}
#hmc_fit_list_misspecify <- readRDS("data/Case1_MultiCause/output/hmc_fit_list_misspecify_Case1.RData")
estimated_y_hmc_list_misspecify <- rep(list(list()), K)
CE_list_misspecify <- list()
means_hmc_misspecify <- c()
means_hmc_list_misspecify <- list()
seed = 1
for (num_data_points in ndp) {
  for (data_count in 1:K) {
    samples_hmc_misspecify <- rstan::extract(hmc_fit_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]], parameters_misspecify)
    estimated_y_hmc_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]] <-  mutilated_model_misspecify(mu1 = mean(samples_hmc_misspecify$mu1),
                                                                                 u1_scale = mean(samples_hmc_misspecify$u1_scale),
                                                                                 theta_zero_M = mean(samples_hmc_misspecify$theta_zero_M),
                                                                                 theta_X1M = mean(samples_hmc_misspecify$theta_X1M),
                                                                                 theta_X2M = mean(samples_hmc_misspecify$theta_X2M),
                                                                                 theta_X3M = mean(samples_hmc_misspecify$theta_X3M),
                                                                                 theta_X4M = mean(samples_hmc_misspecify$theta_X4M),
                                                                                 theta_X5M = mean(samples_hmc_misspecify$theta_X5M),
                                                                                 theta_zero_Y = mean(samples_hmc_misspecify$theta_zero_Y),
                                                                                 theta_MY = mean(samples_hmc_misspecify$theta_MY),
                                                                                 theta_U1Y = mean(samples_hmc_misspecify$theta_U1Y),
                                                                                 x1 = x1[1:num_generated_samples],
                                                                                 x2 = x2[1:num_generated_samples],
                                                                                 x3 = x3[1:num_generated_samples],
                                                                                 x4 = x4[1:num_generated_samples],
                                                                                 x5 = x5[1:num_generated_samples],
                                                                                 seed = seed,
                                                                                 num_generated_samples = 1000
    )
      means_hmc_misspecify <- c(means_hmc_misspecify,mean(estimated_y_hmc_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]]))
    # means_hmc_misspecify <- c(means_hmc_misspecify,abs(mean(estimated_y_hmc_list_misspecify[[data_count]][[paste0("num_data_points_",num_data_points)]]) - mean(intv_data_list[[data_count]]$Y)))
  }
  CE_list_misspecify[[paste0("num_data_points_",num_data_points)]] <- means_hmc_misspecify
  #means_hmc_list_misspecify[[paste0("num_data_points_",num_data_points)]] <- means_hmc_misspecify
  means_hmc_misspecify <- c()
}
#saveRDS(CE_list_misspecify, file = "data/Case1_MultiCause/output/CE_list_misspecify_Case1.RData")
#saveRDS(means_hmc_list_misspecify, file = "data/Case1/output/means_hmc_list_misspecify_Case1.RData")
```

# Plug-in 

In this section we want to compare our approach with the plug-in estimator. We have to construct a parametric model for the conditional distributions that appear in the formula of an identifying functional of a causal effect. For case study 1, the do-calculus based formula is as follows:

$$
P_{M_G}(Y | do(\textbf{x}')) = \int_{m, \textbf x} P_{M_G}(Y|m, \textbf{x}) P_{M_G}(m | \textbf{x}') P_{M_G}(\textbf{x}) dm \text{ } d\textbf{x}
$$
The Stan model is as follows:

```{r}
model_str_plug_in <- "
    data {
        int D;
        int<lower=0,upper=1> X1[D];
        int<lower=0,upper=1> X2[D];
        int<lower=0,upper=1> X3[D];
        int<lower=0,upper=1> X4[D];
        int<lower=0,upper=1> X5[D];
        int<lower=0,upper=1> M[D];
        int<lower=0,upper=1> Y[D];
    }
  parameters {
       real theta_zero_X1; 
       real theta_zero_X2; 
       real theta_zero_X3; 
       real theta_zero_X4; 
       real theta_zero_X5; 
       real theta_zero_M; 
       real theta_X1M;
       real theta_X2M; 
       real theta_X3M;
       real theta_X4M;
       real theta_X5M;
       real theta_zero_Y;
       real theta_MY;
       real theta_X1Y;
       real theta_X2Y;
       real theta_X3Y;
       real theta_X4Y;
       real theta_X5Y;
    }

    model {
        //prior over parameters
        theta_zero_X1  ~ normal(0, 10); 
        theta_zero_X2  ~ normal(0, 10); 
        theta_zero_M ~ normal(0, 10); 
        theta_X1M ~ normal(0, 10); 
        theta_X2M ~ normal(0, 10); 
        theta_zero_Y ~ normal(0, 10); 
        theta_MY ~ normal(0, 10); 
        theta_X1Y ~ normal(0, 10); 
        theta_X2Y ~ normal(0, 10); 
        theta_X3Y ~ normal(0, 10);
        theta_X4Y ~ normal(0, 10);
        theta_X5Y ~ normal(0, 10);
        //likelihood
        X1 ~ bernoulli_logit(theta_zero_X1); 
        X2 ~ bernoulli_logit(theta_zero_X2); 
        X3 ~ bernoulli_logit(theta_zero_X3); 
        X4 ~ bernoulli_logit(theta_zero_X4); 
        X5 ~ bernoulli_logit(theta_zero_X5); 
        for(i in 1:D) {
            M[i] ~ bernoulli_logit(theta_zero_M + theta_X1M * X1[i] + theta_X2M * X2[i] + theta_X3M * X3[i] + theta_X4M * X4[i] + theta_X5M * X5[i]);  
            Y[i] ~ bernoulli_logit(theta_zero_Y + theta_MY * M[i] + theta_X1Y * X1[i] + theta_X2Y * X2[i] + theta_X3Y * X3[i] + theta_X4Y * X4[i] + theta_X5Y * X5[i]); 
        }
    }
"
```


```{r, message=FALSE, warning=FALSE}
mod_plug_in <- rstan::stan_model(model_code = model_str_plug_in)
```


# Mutilated model

```{r}
mutilated_model_plug_in <- function(theta_zero_M,theta_X1M,theta_X2M,theta_X3M,theta_X4M,theta_X5M,
                                    theta_zero_Y, theta_MY,
                                    theta_X1Y,theta_X2Y,theta_X3Y,theta_X4Y,theta_X5Y,
                                    x1, x2, x3, x4, x5,
                                    seed, num_generated_samples) {
  set.seed(seed)
  
  X1 <- x1
  X2 <- x2
  X3 <- x3
  X4 <- x4
  X5 <- x5
  
  pm = rep(0, D)
  pm = 1/(1+exp(-theta_zero_M - theta_X1M * X1 - theta_X2M * X2 - theta_X3M * X3 - theta_X4M * X4 - theta_X5M * X5))
  M <- rbinom(n = D, size = 1, prob = pm)
  
  py = rep(0, D)
  py = 1/(1+exp(-theta_zero_Y - theta_MY * M - theta_X1Y * X1 - theta_X2Y * X2 - theta_X3Y * X3 - theta_X4Y * X4 - theta_X5Y * X5))
  Y <- rbinom(n = D, size = 1, prob = py)
  return(Y)
}
```


```{r}
estimated_y_hmc_list_plug_in <- list()
hmc_fit_list_plug_in <- list()
means_hmc_plug_in <- c()
means_hmc_list_plug_in <- list()
start_time <- Sys.time()
for (num_data_points in ndp) {
  print("num_data_points is:")
  print(num_data_points)
  for (data_count in 1:K) {
    print("data_count is:")
    print(data_count)
    data_list <- list(D=num_data_points,
                      X1 = obs_data_list[[data_count]]$X1[1:num_data_points],
                      X2 = obs_data_list[[data_count]]$X2[1:num_data_points],
                      X3 = obs_data_list[[data_count]]$X3[1:num_data_points],
                      X4 = obs_data_list[[data_count]]$X4[1:num_data_points],
                      X5 = obs_data_list[[data_count]]$X5[1:num_data_points],
                      M = obs_data_list[[data_count]]$M[1:num_data_points],
                      Y = obs_data_list[[data_count]]$Y[1:num_data_points])
    #If you get this error (Cluster setup failed. 2 of 2 workers failed to connect.) run these lines:
    # if (Sys.getenv("RSTUDIO") == "1" && !nzchar(Sys.getenv("RSTUDIO_TERM")) &&
    #     Sys.info()["sysname"] == "Darwin") {
    #   parallel:::setDefaultClusterOptions(setup_strategy = "sequential")
    # }
    hmc_fit_list_plug_in[[data_count]] <- rstan::sampling(mod_plug_in, data=data_list, chains = 2, iter = 3000, warmup = 1500, seed = 2, control = list(max_treedepth = 15)) #seed2,5
    samples_hmc_plug_in <- rstan::extract(hmc_fit_list_plug_in[[data_count]], c("theta_zero_X1", "theta_zero_X2","theta_zero_X3","theta_zero_X4","theta_zero_X5",
                                                                                "theta_zero_M","theta_X1M", "theta_X2M","theta_X3M","theta_X4M","theta_X5M",
                                                                                "theta_zero_Y", "theta_MY","theta_X1Y","theta_X2Y","theta_X3Y","theta_X4Y","theta_X5Y"))
    estimated_y_hmc_list_plug_in[[data_count]] <-  mutilated_model_plug_in(
                                            theta_zero_M = mean(samples_hmc_plug_in$theta_zero_M),
                                            theta_X1M = mean(samples_hmc_plug_in$theta_X1M),
                                            theta_X2M = mean(samples_hmc_plug_in$theta_X2M),
                                            theta_X3M = mean(samples_hmc_plug_in$theta_X3M),
                                            theta_X4M = mean(samples_hmc_plug_in$theta_X4M),
                                            theta_X5M = mean(samples_hmc_plug_in$theta_X5M),
                                            theta_zero_Y = mean(samples_hmc_plug_in$theta_zero_Y),
                                            theta_MY = mean(samples_hmc_plug_in$theta_MY),
                                            theta_X1Y = mean(samples_hmc_plug_in$theta_X1Y),
                                            theta_X2Y = mean(samples_hmc_plug_in$theta_X2Y),
                                            theta_X3Y = mean(samples_hmc_plug_in$theta_X3Y),
                                            theta_X4Y = mean(samples_hmc_plug_in$theta_X4Y),
                                            theta_X5Y = mean(samples_hmc_plug_in$theta_X5Y),
                                            x1 = x1[1:num_generated_samples],
                                            x2 = x2[1:num_generated_samples],
                                            x3 = x3[1:num_generated_samples],
                                            x4 = x4[1:num_generated_samples],
                                            x5 = x5[1:num_generated_samples],
                                            seed = seed,
                                            num_generated_samples = num_generated_samples
    )
    means_hmc_plug_in <- c(means_hmc_plug_in,abs(mean(estimated_y_hmc_list_plug_in[[data_count]]) - mean(intv_data_list[[data_count]]$Y)))
    
  }
  means_hmc_list_plug_in[[paste0("num_data_points_",num_data_points)]] <- means_hmc_plug_in
  print("means_hmc_list_plug_in is:")
  print(means_hmc_list_plug_in)
  means_hmc_plug_in <- c()
}
end_time <- Sys.time()
end_time - start_time
#saveRDS(means_hmc_list_plug_in, file = "data/Case1/output/means_hmc_list_plug_in_Case1.RData")
```